---
title: "Supplement 2: Simulations — Inverse Probability Weights for Quasi-Continuous Ordinal Exposures with a Binary Outcome: Method Comparison and Case Study"
author: "Sack, Daniel E, Shepherd, Bryan E, Audet, Carolyn M, De Schact, Caroline, Samuels, Lauren R"
date: "<small>Updated `r Sys.Date()` for American Journal of Epidemiology</small>"
output:
  pdf_document: default
description: "Ordinal Propsensity Score Analysis"
bibliography: references.bib
csl: american-journal-of-epidemiology.csl
---
# Setup

```{r setup, include=FALSE}
# full code available at https://github.com/dannysack/gen_prop_wts

source("./orm.wt.R") # loads tidyverse, rms, and mice libraries
library(WeightIt)
library(MatchThem)
library(cobalt)
library(lme4)
library(kableExtra)
library(ggpubr)
library(parallel)
library(furrr)
library(foreach)
library(doParallel)
library(extrafont)
library(ggdist)
library(survey)
loadfonts()
knitrSet(lang='markdown', fig.path='png_pdf/', fig.align='center', w=9, h=8, cache=TRUE)
options(knitr.kable.NA = '')

# set seed across all all streams for parallel processing
set.seed(1111, kind = "L'Ecuyer-CMRG")

# set theme for plots
theme <- theme_pubr() +
  theme(legend.position = "bottom",
               legend.key = element_rect(fill = NA, color = NA),
               text = element_text(family = "Arial"), 
               axis.line = element_line(), 
               axis.text = element_text(family = "Arial", color = "black"),
               strip.background = element_rect(fill = "grey95"))
```

# Generate Data

Generating data per stipulations of Naimi, Moodie, Auger, Kaufman, Epidemiology 2014; 25: 292-299 [@naimi2014].

To generate the skewed version of `mage`, which we define as `mage_g`, we started with a gamma distribution with shape equal to `0.5` and scale equal to `500`. We then shifted the mean to `0` and changed it from right skewed to left skew (to make it a more appropriate skew for maternal age). We then normalized the standard deviation to `1` so that we could stretch the distribution to have the same standard deviation as `mage`. Finally, we set the mean of `mage_g` to the mean of `mage` and reallocated any `mage_g` values of less than `11` to the mean age. To generate the updated $\mu$, $\mu_2$, we increased the correlation between `mage_g` and $\mu_2$ from `0.025` to `0.25`.

```{r data_gen}
# function to generate data per Naimi et al. specifications, 
# but make the exposure ordinal instead of continuous via rounding
sim_data <- function(n) {
  # draw maternal age from normal distribution
  mage <- rnorm(n, 29.84, sqrt(21.60))
  
  # maternal age from gamma distribution for a conditionally normal 
  # but marginally not normal covariate
  m1 <- rgamma(n, shape = 0.5, scale = 5000) # make very skewed distribution, sims is 5 and 5
  m2 <- (m1 - mean(m1)) * -1 # shift the mean to zero and 
  # flip the direction of the skew (so left instead of right skewed)
  m3 <- m2 / sd(m2) # makes sd 1
  m4 <- m3 * sd(mage) # stretch so it has the sd of mage
  mage_g <- m4 + mean(mage) # make it have the same mean as mage
  mage_g[mage_g < 11] <- mean(mage_g) # make any values < 0 the mean, 
  # since maternal age cannot really be under 11

  # draw paternal age from normal distribution
  page <- rnorm(n, 32.52, sqrt(30.45))

  # establish parity with same parameters as Naimi et al.
  parityA <- runif(n)
  parity <- ifelse(parityA <= 0.24, 2,
               ifelse(parityA <= 0.24 + 0.07, 3,
                      ifelse(parityA <= 0.24 + 0.07 + 0.02, 4,
                             ifelse(parityA <= 0.24 + 0.07 + 0.02 + 0.02, 5, 1))))
  parity2 <- ifelse(parity == 2, 1, 0)
  parity3 <- ifelse(parity == 3, 1, 0)
  parity4 <- ifelse(parity == 4, 1, 0)
  parity5 <- ifelse(parity == 5, 1, 0)

  # mu w/o strong correlation with maternal age
  mu_un <- (0.025 * mage) + (0.0025 * page) + (0.00125 * mage * page) - 
  (0.21 * parity2) - (0.22 * parity3) - (0.45 * parity4) - (0.45 * parity5)
  
  # mu w/ gamma distributed maternal age and strong correlation
  mu_g <- (0.25 * mage_g) + (0.0025 * page) + (0.00125 * mage_g * page) - 
  (0.21 * parity2) - (0.22 * parity3) - (0.45 * parity4) - (0.45 * parity5)

  # normal exposure distribution, but round so it's ordinal to nearest 0.1
  x1 <- round(15 + mu_un + rnorm(n, 0, sqrt(2)), 1)
  
  # normal exposure distribution, but marginally not normal, but round so it's ordinal to nearest 0.1
  x2 <- round(15 + mu_g + rnorm(n, 0, sqrt(2)), 1)

  # poisson exposure distribution, but round so it's ordinal to nearest 0.1
  x3 <- round(pmax(rpois(n, mu_un) + rnorm(n,0,1), 0), 1)
  
  # normal exposure distribution, but round so it's ordinal to nearest 1
  x4 <- round(15 + mu_un + rnorm(n, 0, sqrt(2)))
  
  # normal exposure distribution, but marginally not normal, but round so it's ordinal to nearest 1
  x5 <- round(15 + mu_g + rnorm(n, 0, sqrt(2)))

  # poisson exposure distribution, but round so it's ordinal to nearest 1
  x6 <- round(pmax(rpois(n, mu_un) + rnorm(n,0,1), 0))
  
  # now replicate Naimi's continuous exposures
  n_x1 <- 15 + mu_un + rnorm(n, 0, sqrt(2))
  # n_x1 <- rnorm(n, 15 + mu_un, 1.5) # 
  # <- I think this is how they technically did it, but they are the same.
  
  n_x2 <- pmax(rpois(n, mu_un) + rnorm(n,0,1), 0)

  # outcome normal exposure distribution, uncorrelated with maternal age
  y1 <- rbinom(n, 1, (1  + exp(-(-11.5 + log(1.25) * x1 + log(1.7) * sqrt(mage) + log(1.5) * sqrt(page) +
                        log(0.75) * parity2 + log(0.8) * parity3 + log(0.85) * parity4 + log(0.9) *parity5)))^(-1))
  
  # normal exposure distribution, but marginally not normal
  y2 <- rbinom(n, 1, (1  + exp(-(-13 + log(1.25) * x2 + log(1.7) * sqrt(mage_g) + 
                                   log(1.5) * sqrt(page) + log(0.75) * parity2 + 
                                   log(0.8) * parity3 + log(0.85) * parity4 + 
                                   log(0.9) *parity5)))^(-1))

  # outcome poisson exposure distribution, uncorrelated with maternal age
  y3 <- rbinom(n, 1, (1 + exp(-(-8.05 + log(1.25) * x3 + log(1.7) * sqrt(mage) + 
                                  log(1.5) * sqrt(page) + log(0.75) * parity2 + 
                                  log(0.8) * parity3 + log(0.85) * parity4 + 
                                  log(0.9) * parity5)))^(-1))
  
  # outcome normal exposure distribution, uncorrelated with maternal age
  y4 <- rbinom(n, 1, (1  + exp(-(-11.5 + log(1.25) * x4 + log(1.7) * sqrt(mage) + log(1.5) * sqrt(page) +
                        log(0.75) * parity2 + log(0.8) * parity3 + log(0.85) * parity4 + log(0.9) *parity5)))^(-1))
  
  # normal exposure distribution, but marginally not normal
  y5 <- rbinom(n, 1, (1  + exp(-(-13 + log(1.25) * x5 + log(1.7) * sqrt(mage_g) + 
                                   log(1.5) * sqrt(page) + log(0.75) * parity2 + 
                                   log(0.8) * parity3 + log(0.85) * parity4 + 
                                   log(0.9) *parity5)))^(-1))

  # outcome poisson exposure distribution, uncorrelated with maternal age
  y6 <- rbinom(n, 1, (1 + exp(-(-8.05 + log(1.25) * x6 + log(1.7) * sqrt(mage) + 
                                  log(1.5) * sqrt(page) + log(0.75) * parity2 + 
                                  log(0.8) * parity3 + log(0.85) * parity4 + 
                                  log(0.9) * parity5)))^(-1))
  
  # replicate Naimi's outcomes given continuous exposures
  n_y1 <- rbinom(n, 1, (1  + exp(-(-11.5 + log(1.25) * n_x1 + log(1.7) * sqrt(mage) + 
                                     log(1.5) * sqrt(page) + log(0.75) * parity2 + 
                                     log(0.8) * parity3 + log(0.85) * parity4 + 
                                     log(0.9) * parity5)))^(-1))
  
  n_y2 <- rbinom(n, 1, (1 + exp(-(-8.05 + log(1.25) * n_x2 + log(1.7) * sqrt(mage) + 
                                    log(1.5) * sqrt(page) + log(0.75) * parity2 + 
                                    log(0.8) * parity3 + log(0.85) * parity4 + 
                                    log(0.9) * parity5)))^(-1))

  # create df with all covariates as output
  data.frame(mage, mage_g, page, parity2, parity3, parity4, parity5, 
             x1, x2, x3, x4, x5, x6, n_x1, n_x2, y1, y2, y3, y4, y5, y6, n_y1, n_y2)
}

# to check outcome prevalence with different intercepts
#table1::table1(~ factor(y1) + factor(y2) + factor(y3) + factor(y4) + factor(y5) + factor(y6), data = sim_data(n = 3000000))

# test exposure distributions
# test <- sim_data(n = 30000)
# hist(test$x1)
# hist(test$x2)
# hist(test$x3)
# hist(test$x4)
# hist(test$x5)
# hist(test$x6)
```

# Simulations

Do 3000 simulations and generate weights for each simulation, combine each simulation into one long dataframe with weights and list and simulation number. Generate weights with OLS, CBGPS, QB10, QB15, QB20, and CPM.

For *X*~2~, we updated the intercept values (from -11.5 [*X*~1~] to -11.4 [*X*~2~]) to maintain a marginal probability of the outcome of approximately 0.08 with the updated exposure distributions.

We calculated the sIPW denominators using the following regression formula per Naimi et al.'s specifications, where *C* are the selected confounders, with *mage_g* instead of *mage* when i $\epsilon$ {2} and binned exposures instead of *X*~i~ when calculating QB weights:

E(*X*~i~ \| *C*) = $\beta_{1}$(mage) + $\beta_{2}$(page) + $\beta_{3}$(mage\*page) + $\beta_{4}$(parity2) + $\beta_{5}$(parity3) + $\beta_{6}$(parity4) + $\beta_{7}$(parity5)

The range, median, and mean of the exposure distributions are in Supplemental Table 1.2.

```{r sim, eval = FALSE}
# register clusters (use 7 cores)
registerDoParallel(detectCores() - 1)

# number of reps (will go up to 3000, can tinker to test things)
n = 3000

# now generate weights 
# (will generate weights in each simulated dataset individually)
sims <- foreach(i = 1:n, .inorder = FALSE, .errorhandling = "remove") %dopar% {
  # first need to generate data and quantile binned exposures
  df <- sim_data(n = 1500) %>% 
  mutate(x1_qb10 = as.numeric(cut2(x1, g = 10)),
         x2_qb10 = as.numeric(cut2(x2, g = 10)),
         x3_qb10 = as.numeric(cut2(x3, g = 10)),
         x4_qb10 = as.numeric(cut2(x4, g = 10)),
         x1_qb15 = as.numeric(cut2(x1, g = 15)),
         x2_qb15 = as.numeric(cut2(x2, g = 15)),
         x3_qb15 = as.numeric(cut2(x3, g = 15)),
         x4_qb15 = as.numeric(cut2(x4, g = 15)),
         x1_qb20 = as.numeric(cut2(x1, g = 20)),
         x2_qb20 = as.numeric(cut2(x2, g = 20)),
         x3_qb20 = as.numeric(cut2(x3, g = 20)),
         x4_qb20 = as.numeric(cut2(x4, g = 20)))
  
  # start by creating formulas
  x1_formula <- formula(x1 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x2_formula <- formula(x2 ~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + parity5)
  x3_formula <- formula(x3 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x4_formula <- formula(x4 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x5_formula <- formula(x5 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x6_formula <- formula(x6 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)

  # use WeightIt package to generate OLS and CBGPS weights

  # OLS
  x1_ols_wts <- weightit(x1_formula, df %>% filter(!is.na(x1)), method = "ps")$weights
  x2_ols_wts <- weightit(x2_formula, df %>% filter(!is.na(x2)), method = "ps")$weights
  x3_ols_wts <- weightit(x3_formula, df %>% filter(!is.na(x3)), method = "ps")$weights
  x4_ols_wts <- weightit(x4_formula, df %>% filter(!is.na(x4)), method = "ps")$weights
  x5_ols_wts <- weightit(x5_formula, df %>% filter(!is.na(x5)), method = "ps")$weights
  x6_ols_wts <- weightit(x6_formula, df %>% filter(!is.na(x6)), method = "ps")$weights

  #CBGPS
  x1_cbgps_wts <- weightit(x1_formula, df %>% filter(!is.na(x1)), method = "cbps", 
                           over = FALSE)$weights
  x2_cbgps_wts <- weightit(x2_formula, df %>% filter(!is.na(x2)), method = "cbps", 
                           over = FALSE)$weights
  x3_cbgps_wts <- weightit(x3_formula, df %>% filter(!is.na(x3)), method = "cbps", 
                           over = FALSE)$weights
  x4_cbgps_wts <- weightit(x4_formula, df %>% filter(!is.na(x4)), method = "cbps", 
                           over = FALSE)$weights
  x5_cbgps_wts <- weightit(x5_formula, df %>% filter(!is.na(x5)), method = "cbps", 
                           over = FALSE)$weights
  x6_cbgps_wts <- weightit(x6_formula, df %>% filter(!is.na(x6)), method = "cbps", 
                           over = FALSE)$weights
  
  #npCBGPS
  x1_npcbgps_wts <- weightit(x1_formula, df %>% filter(!is.na(x1)), method = "npcbps", 
                           over = FALSE)$weights
  x2_npcbgps_wts <- weightit(x2_formula, df %>% filter(!is.na(x2)), method = "npcbps", 
                           over = FALSE)$weights
  x3_npcbgps_wts <- weightit(x3_formula, df %>% filter(!is.na(x3)), method = "npcbps", 
                           over = FALSE)$weights
  x4_npcbgps_wts <- weightit(x4_formula, df %>% filter(!is.na(x4)), method = "npcbps", 
                           over = FALSE)$weights
  x5_npcbgps_wts <- weightit(x5_formula, df %>% filter(!is.na(x5)), method = "npcbps", 
                           over = FALSE)$weights
  x6_npcbgps_wts <- weightit(x6_formula, df %>% filter(!is.na(x6)), method = "npcbps", 
                           over = FALSE)$weights

  # use orm.wt file to create quantile binning and OLR weights
  
  
  # only doing QB for x1-x3, because at smaller number of categories, they are the same thing
  # QB10
  x1_qb10_wts <- orm.wt(object = df %>% filter(!is.na(x1)),
                    exposure = "x1_qb10",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x2_qb10_wts <- orm.wt(object = df %>% filter(!is.na(x2)),
                    exposure = "x2_qb10",
                    cov_form = "~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x3_qb10_wts <- orm.wt(object = df %>% filter(!is.na(x3)),
                    exposure = "x3_qb10",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  
  # QB15
  x1_qb15_wts <- orm.wt(object = df %>% filter(!is.na(x1)),
                    exposure = "x1_qb15",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x2_qb15_wts <- orm.wt(object = df %>% filter(!is.na(x2)),
                    exposure = "x2_qb15",
                    cov_form = "~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x3_qb15_wts <- orm.wt(object = df %>% filter(!is.na(x3)),
                    exposure = "x3_qb15",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  
  # QB20
  x1_qb20_wts <- orm.wt(object = df %>% filter(!is.na(x1)),
                    exposure = "x1_qb20",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x2_qb20_wts <- orm.wt(object = df %>% filter(!is.na(x2)),
                    exposure = "x2_qb20",
                    cov_form = "~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x3_qb20_wts <- orm.wt(object = df %>% filter(!is.na(x3)),
                    exposure = "x3_qb20",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()

  # OLR
  x1_olr_wts <- orm.wt(object = df %>% filter(!is.na(x1)),
                    exposure = "x1",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x2_olr_wts <- orm.wt(object = df %>% filter(!is.na(x2)),
                    exposure = "x2",
                    cov_form = "~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x3_olr_wts <- orm.wt(object = df %>% filter(!is.na(x3)),
                    exposure = "x3",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x4_olr_wts <- orm.wt(object = df %>% filter(!is.na(x4)),
                    exposure = "x4",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x5_olr_wts <- orm.wt(object = df %>% filter(!is.na(x5)),
                    exposure = "x5",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x6_olr_wts <- orm.wt(object = df %>% filter(!is.na(x6)),
                    exposure = "x6",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  
  # create final dataframe
  data <- data.frame(i, df, 
                     x1_ols_wts, x2_ols_wts, x3_ols_wts, x4_ols_wts, x5_ols_wts, x6_ols_wts,
                     x1_cbgps_wts, x2_cbgps_wts, x3_cbgps_wts, x4_cbgps_wts, x5_cbgps_wts, x6_cbgps_wts,
                     x1_npcbgps_wts, x2_npcbgps_wts, x3_npcbgps_wts, x4_npcbgps_wts, x5_npcbgps_wts, x6_npcbgps_wts,
                     x1_qb10_wts, x2_qb10_wts, x3_qb10_wts, 
                     x1_qb15_wts, x2_qb15_wts, x3_qb15_wts, 
                     x1_qb20_wts, x2_qb20_wts, x3_qb20_wts, 
                     x1_olr_wts, x2_olr_wts, x3_olr_wts, x4_olr_wts, x5_olr_wts, x6_olr_wts)
}

# add in simluation for anything less than 3000, with new seed across all all streams for parallel processing (from 1111 to 11111)
set.seed(11111, kind = "L'Ecuyer-CMRG")
n_extra <- 3000 - length(sims)
sims2 <- foreach(i = 1:n_extra, .inorder = FALSE, .errorhandling = "remove") %dopar% {
  # first need to generate data and quantile binned exposures
  df <- sim_data(n = 1500) %>% 
  mutate(x1_qb10 = as.numeric(cut2(x1, g = 10)),
         x2_qb10 = as.numeric(cut2(x2, g = 10)),
         x3_qb10 = as.numeric(cut2(x3, g = 10)),
         x4_qb10 = as.numeric(cut2(x4, g = 10)),
         x1_qb15 = as.numeric(cut2(x1, g = 15)),
         x2_qb15 = as.numeric(cut2(x2, g = 15)),
         x3_qb15 = as.numeric(cut2(x3, g = 15)),
         x4_qb15 = as.numeric(cut2(x4, g = 15)),
         x1_qb20 = as.numeric(cut2(x1, g = 20)),
         x2_qb20 = as.numeric(cut2(x2, g = 20)),
         x3_qb20 = as.numeric(cut2(x3, g = 20)),
         x4_qb20 = as.numeric(cut2(x4, g = 20)))
  
  # start by creating formulas
  x1_formula <- formula(x1 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x2_formula <- formula(x2 ~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + parity5)
  x3_formula <- formula(x3 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x4_formula <- formula(x4 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x5_formula <- formula(x5 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x6_formula <- formula(x6 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)

  # use WeightIt package to generate OLS and CBGPS weights

  # OLS
  x1_ols_wts <- weightit(x1_formula, df %>% filter(!is.na(x1)), method = "ps")$weights
  x2_ols_wts <- weightit(x2_formula, df %>% filter(!is.na(x2)), method = "ps")$weights
  x3_ols_wts <- weightit(x3_formula, df %>% filter(!is.na(x3)), method = "ps")$weights
  x4_ols_wts <- weightit(x4_formula, df %>% filter(!is.na(x4)), method = "ps")$weights
  x5_ols_wts <- weightit(x5_formula, df %>% filter(!is.na(x5)), method = "ps")$weights
  x6_ols_wts <- weightit(x6_formula, df %>% filter(!is.na(x6)), method = "ps")$weights

  #CBGPS
  x1_cbgps_wts <- weightit(x1_formula, df %>% filter(!is.na(x1)), method = "cbps", 
                           over = FALSE)$weights
  x2_cbgps_wts <- weightit(x2_formula, df %>% filter(!is.na(x2)), method = "cbps", 
                           over = FALSE)$weights
  x3_cbgps_wts <- weightit(x3_formula, df %>% filter(!is.na(x3)), method = "cbps", 
                           over = FALSE)$weights
  x4_cbgps_wts <- weightit(x4_formula, df %>% filter(!is.na(x4)), method = "cbps", 
                           over = FALSE)$weights
  x5_cbgps_wts <- weightit(x5_formula, df %>% filter(!is.na(x5)), method = "cbps", 
                           over = FALSE)$weights
  x6_cbgps_wts <- weightit(x6_formula, df %>% filter(!is.na(x6)), method = "cbps", 
                           over = FALSE)$weights
  
  #npCBGPS
  x1_npcbgps_wts <- weightit(x1_formula, df %>% filter(!is.na(x1)), method = "npcbps", 
                           over = FALSE)$weights
  x2_npcbgps_wts <- weightit(x2_formula, df %>% filter(!is.na(x2)), method = "npcbps", 
                           over = FALSE)$weights
  x3_npcbgps_wts <- weightit(x3_formula, df %>% filter(!is.na(x3)), method = "npcbps", 
                           over = FALSE)$weights
  x4_npcbgps_wts <- weightit(x4_formula, df %>% filter(!is.na(x4)), method = "npcbps", 
                           over = FALSE)$weights
  x5_npcbgps_wts <- weightit(x5_formula, df %>% filter(!is.na(x5)), method = "npcbps", 
                           over = FALSE)$weights
  x6_npcbgps_wts <- weightit(x6_formula, df %>% filter(!is.na(x6)), method = "npcbps", 
                           over = FALSE)$weights

  # use orm.wt file to create quantile binning and OLR weights
  
  
  # only doing QB for x1-x3, because at smaller number of categories, they are the same thing
  # QB10
  x1_qb10_wts <- orm.wt(object = df %>% filter(!is.na(x1)),
                    exposure = "x1_qb10",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x2_qb10_wts <- orm.wt(object = df %>% filter(!is.na(x2)),
                    exposure = "x2_qb10",
                    cov_form = "~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x3_qb10_wts <- orm.wt(object = df %>% filter(!is.na(x3)),
                    exposure = "x3_qb10",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  
  # QB15
  x1_qb15_wts <- orm.wt(object = df %>% filter(!is.na(x1)),
                    exposure = "x1_qb15",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x2_qb15_wts <- orm.wt(object = df %>% filter(!is.na(x2)),
                    exposure = "x2_qb15",
                    cov_form = "~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x3_qb15_wts <- orm.wt(object = df %>% filter(!is.na(x3)),
                    exposure = "x3_qb15",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  
  # QB20
  x1_qb20_wts <- orm.wt(object = df %>% filter(!is.na(x1)),
                    exposure = "x1_qb20",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x2_qb20_wts <- orm.wt(object = df %>% filter(!is.na(x2)),
                    exposure = "x2_qb20",
                    cov_form = "~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x3_qb20_wts <- orm.wt(object = df %>% filter(!is.na(x3)),
                    exposure = "x3_qb20",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()

  # OLR
  x1_olr_wts <- orm.wt(object = df %>% filter(!is.na(x1)),
                    exposure = "x1",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x2_olr_wts <- orm.wt(object = df %>% filter(!is.na(x2)),
                    exposure = "x2",
                    cov_form = "~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x3_olr_wts <- orm.wt(object = df %>% filter(!is.na(x3)),
                    exposure = "x3",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x4_olr_wts <- orm.wt(object = df %>% filter(!is.na(x4)),
                    exposure = "x4",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x5_olr_wts <- orm.wt(object = df %>% filter(!is.na(x5)),
                    exposure = "x5",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  x6_olr_wts <- orm.wt(object = df %>% filter(!is.na(x6)),
                    exposure = "x6",
                    cov_form = "~ mage + page + mage*page + parity2 + parity3 + parity4 + 
                    parity5") %>%
    unlist()
  
  # create final dataframe
  data <- data.frame(i, df, 
                     x1_ols_wts, x2_ols_wts, x3_ols_wts, x4_ols_wts, x5_ols_wts, x6_ols_wts,
                     x1_cbgps_wts, x2_cbgps_wts, x3_cbgps_wts, x4_cbgps_wts, x5_cbgps_wts, x6_cbgps_wts,
                     x1_npcbgps_wts, x2_npcbgps_wts, x3_npcbgps_wts, x4_npcbgps_wts, x5_npcbgps_wts, x6_npcbgps_wts,
                     x1_qb10_wts, x2_qb10_wts, x3_qb10_wts, 
                     x1_qb15_wts, x2_qb15_wts, x3_qb15_wts, 
                     x1_qb20_wts, x2_qb20_wts, x3_qb20_wts, 
                     x1_olr_wts, x2_olr_wts, x3_olr_wts, x4_olr_wts, x5_olr_wts, x6_olr_wts)
}

# combine
sims <- append(sims, sims2)

# save simulation output
Save(sims)
```

```{r load_sims, cache.lazy=FALSE}
# load simulation data
Load(sims)

# make it a dataframe
df <- sims %>% bind_rows(.id = "i")

# create a new dataset with 4.5 million rows to simulate the truth
set.seed(1111)
df_msm_sim <- sim_data(n = nrow(df))
```

```{r msm_truth, eval = FALSE}
# Marginal Structural Model "Truth"
getMeanProb_MSM <- function(dat, val, xnum) {
    # returns the mean outcome probability (that is, an estimate of E[Y(t)]) at exposure value [val]
    if (xnum == "x1" | xnum == "x4") {
        alpha <- -11.5   
        magevar <- "mage"
    } else if (xnum == "x2" | xnum == "x5") {
        alpha <- -13   
        magevar <- "mage_g"
    } else if (xnum == "x3" | xnum == "x6") {
        alpha <- -8.05
        magevar <- "mage"
    }
   
    lp <-
        alpha +
        log(1.25) * (val) +
        log(1.7) * sqrt(dat[[magevar]])+
        log(1.5) * sqrt(dat$page) +
        log(0.75) * dat$parity2 +
        log(0.8) * dat$parity3 +
        log(0.85) * dat$parity4 +
        log(0.9) * dat$parity5
    prob <- plogis(lp)
    mean(prob)
}

# run it with parallel processing

# register clusters (use 6 cores because 6 processes)
registerDoParallel(6)

# now generate weights 
msm_truths <- foreach(i = 1:6, .inorder = FALSE, .errorhandling = "remove") %dopar% {
  #exposures
  exps <- c("x1", "x2", "x3", "x4", "x5", "x6")
  
  # each is a vector of estimates of E[Y(t)]'s: one for each unique t in the original dataset 
  # (excluding repeats)
  probs <- lapply(unique(df_msm_sim[[exps[i]]]), 
                  function(x) getMeanProb_MSM(df_msm_sim, x, xnum = exps[i]))
}

# save it
Save(msm_truths)
```

```{r austin_truth}
# pull in MSM truth, because it  will be too big to run each time
Load(msm_truths)
x1_truth_key <- tibble(x1 = unique(df_msm_sim$x1), prob_x1 = unlist(msm_truths[1]))
x2_truth_key <- tibble(x2 = unique(df_msm_sim$x2), prob_x2 = unlist(msm_truths[2]))
x3_truth_key <- tibble(x3 = unique(df_msm_sim$x3), prob_x3 = unlist(msm_truths[3]))
x4_truth_key <- tibble(x4 = unique(df_msm_sim$x4), prob_x4 = unlist(msm_truths[4]))
x5_truth_key <- tibble(x5 = unique(df_msm_sim$x5), prob_x5 = unlist(msm_truths[5]))
x6_truth_key <- tibble(x6 = unique(df_msm_sim$x6), prob_x6 = unlist(msm_truths[6]))

# now need to link truths with exposure they match
x_truths <- df_msm_sim %>%
  select(x1, x2, x3, x4, x5, x6)

# put in truths
x_truths <- left_join(x_truths, x1_truth_key, by = "x1")
x_truths <- left_join(x_truths, x2_truth_key, by = "x2")
x_truths <- left_join(x_truths, x3_truth_key, by = "x3")
x_truths <- left_join(x_truths, x4_truth_key, by = "x4")
x_truths <- left_join(x_truths, x5_truth_key, by = "x5")
x_truths <- left_join(x_truths, x6_truth_key, by = "x6")

# show that there are no non-missing values of prob_x1:prob_x6 after joining
sum(is.na(x_truths$prob_x1), is.na(x_truths$prob_x2), is.na(x_truths$prob_x3),
    is.na(x_truths$prob_x4), is.na(x_truths$prob_x5), is.na(x_truths$prob_x6))
sum(!is.na(x_truths$prob_x1), !is.na(x_truths$prob_x2), !is.na(x_truths$prob_x3),
    !is.na(x_truths$prob_x4), !is.na(x_truths$prob_x5), !is.na(x_truths$prob_x6))/6

# Our MSM: logit{E[Y(t)]}= b0 + b1*t
#     The warning is OK!
msm_x1 <- glm(x_truths$prob_x1 ~ x_truths$x1, family= binomial)
true_x1 <- coef(msm_x1)["x_truths$x1"] %>% unname()

msm_x2 <- glm(x_truths$prob_x2 ~ x_truths$x2, family= binomial)
true_x2 <- coef(msm_x2)["x_truths$x2"] %>% unname()

msm_x3 <- glm(x_truths$prob_x3 ~ x_truths$x3, family= binomial)
true_x3 <- coef(msm_x3)["x_truths$x3"] %>% unname()

msm_x4 <- glm(x_truths$prob_x4 ~ x_truths$x4, family= binomial)
true_x4 <- coef(msm_x4)["x_truths$x4"] %>% unname()

msm_x5 <- glm(x_truths$prob_x5 ~ x_truths$x5, family= binomial)
true_x5 <- coef(msm_x5)["x_truths$x5"] %>% unname()

msm_x6 <- glm(x_truths$prob_x6 ~ x_truths$x6, family= binomial)
true_x6 <- coef(msm_x6)["x_truths$x6"] %>% unname()

# Austin, 2018 approach to finding the truth
# find the true probability, across all 4.5 million observations at each decile (seq(0.1, 0.9, 0.1))
# the the expected probabilities are found below in the bias chunk
getMeanProb <- function(dat, val, xnum) {
    if (xnum == 1 | xnum == 4) {
        alpha <- -11.5    
        magevar <- "mage"
    } else if (xnum == 2 | xnum == 5) {
        alpha <- -13   
        magevar <- "mage_g"
    } else if (xnum == 3 | xnum == 6) {
        alpha <- -8.05
        magevar <- "mage"
    }
    lp <- alpha + 
        log(1.25) * (val) + 
        log(1.7) * sqrt(dat[[magevar]])+ 
        log(1.5) * sqrt(dat$page) +
        log(0.75) * dat$parity2 + 
        log(0.8) * dat$parity3 + 
        log(0.85) * dat$parity4 + 
        log(0.9) * dat$parity5
    # p = (1 + 1/odds)^(-1) 
    prob <- (1 + 1/exp(lp))^(-1)
    mean(prob)
}

# x1
true2_x1_qs <- map_dbl(seq(0.1, 0.9, 0.1), ~ getMeanProb(dat = df_msm_sim, 
                                                         val = quantile(df_msm_sim$x1, .x), xnum = 1))

# x2
true2_x2_qs <- map_dbl(seq(0.1, 0.9, 0.1), ~ getMeanProb(dat = df_msm_sim, 
                                                         val = quantile(df_msm_sim$x2, .x), xnum = 2))

# x3
true2_x3_qs <- map_dbl(seq(0.1, 0.9, 0.1), ~ getMeanProb(dat = df_msm_sim, 
                                                         val = quantile(df_msm_sim$x3, .x), xnum = 3))

# x4
true2_x4_qs <- map_dbl(seq(0.1, 0.9, 0.1), ~ getMeanProb(dat = df_msm_sim, 
                                                         val = quantile(df_msm_sim$x4, .x), xnum = 4))

# x5
true2_x5_qs <- map_dbl(seq(0.1, 0.9, 0.1), ~ getMeanProb(dat = df_msm_sim, 
                                                         val = quantile(df_msm_sim$x5, .x), xnum = 5))

# x6
true2_x6_qs <- map_dbl(seq(0.1, 0.9, 0.1), ~ getMeanProb(dat = df_msm_sim, 
                                                         val = quantile(df_msm_sim$x6, .x), xnum = 6))
```

### Supplemental Table 2.1 - Updated Exposure Levels

```{r exp_levels}
# get number of exposure levels across simulations
exp_levels <- function(data) {
  x1 <- n_distinct(data$x1)
  x2 <- n_distinct(data$x2)
  x3 <- n_distinct(data$x3)
  x4 <- n_distinct(data$x4)
  x5 <- n_distinct(data$x5)
  x6 <- n_distinct(data$x6)
  
  data.frame(x1, x2, x3, x4, x5, x6)
}

suptab2 <- map_df(sims, ~ exp_levels(.x)) %>% summary()
kable(suptab2) %>%
  kable_classic(html_font = "Arial", full_width = FALSE)
```

### Supplemental Table 2.2 - Dose Response Deciles

```{r deciles}
# create deciles quantiles for each Austin approach
x1_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x1, .x))

x2_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x2, .x))

x3_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x3, .x))

x4_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x4, .x))

x5_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x5, .x))

x6_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x6, .x))

# print table of decile values
dec_tab <- tibble(Decile = c(1:9),
                  X1 = x1_quants,
                  X2 = x2_quants,
                  X3 = x3_quants,
                  X4 = x4_quants,
                  X5 = x5_quants,
                  X6 = x6_quants)
kable(dec_tab) %>%
  kable_classic(html_font = "Arial", full_width = FALSE)
```

# Recreating Distributions from Naimi et al.

## Supplemental Table 2.3 - Simulation Descriptive Statistics

```{r tab1}
# recreate table 1
tab1 <- tibble(`Variable (Distribution)` = c("Maternal Age (normal)",
                                             "Maternal Age (skewed)",
                                             "Paternal Age (normal)",
                                             "Parity (Poisson)",
                                             "2",
                                             "3",
                                             "4",
                                             "5+",
                                             "X1 (normal, naimi) - rounded to 0.1",
                                             "X2 (normal, skewed) - rounded to 0.1",
                                             "X3 (Poisson, naimi) - rounded to 0.1",
                                             "X4 (normal, naimi) - rounded to 1",
                                             "X5 (normal, skewed) - rounded to 1",
                                             "X6 (Poisson, naimi) - rounded to 1",
                                             "Y1 (Bernoulli, naimi)",
                                             "Y2 (Bernoulli, skewed)",
                                             "Y3 (Bernoulli, naimi)",
                                             "Y4 (Bernoulli, naimi)",
                                             "Y5 (Bernoulli, skewed)",
                                             "Y6 (Bernoulli, naimi)",
                                             "Naimi Homoscedastic X",
                                             "Naimi Heteroscedastic X",
                                             "Naimi Homoscedastic Y",
                                             "Naimi Heteroscedastic Y"),
               Mean = c(mean(df$mage),
                        mean(df$mage_g),
                        mean(df$page),
                        NA,
                        mean(df$parity2),
                        mean(df$parity3),
                        mean(df$parity4),
                        mean(df$parity5),
                        mean(df$x1),
                        mean(df$x2),
                        mean(df$x3, na.rm = TRUE),
                        mean(df$x4, na.rm = TRUE),
                        mean(df$x5, na.rm = TRUE),
                        mean(df$x6, na.rm = TRUE),
                        mean(df$y1),
                        mean(df$y2),
                        mean(df$y3, na.rm = TRUE),
                        mean(df$y4, na.rm = TRUE),
                        mean(df$y5, na.rm = TRUE),
                        mean(df$y6, na.rm = TRUE),
                        mean(df$n_x1),
                        mean(df$n_x2, na.rm = TRUE),
                        mean(df$n_y1),
                        mean(df$n_y2, na.rm = TRUE)),
               Variance = c(var(df$mage),
                        var(df$mage_g),
                        var(df$page),
                        NA,
                        var(df$parity2),
                        var(df$parity3),
                        var(df$parity4),
                        var(df$parity5),
                        var(df$x1),
                        var(df$x2),
                        var(df$x3, na.rm = TRUE),
                        var(df$x4, na.rm = TRUE),
                        var(df$x5, na.rm = TRUE),
                        var(df$x6, na.rm = TRUE),
                        var(df$y1),
                        var(df$y2),
                        var(df$y3, na.rm = TRUE),
                        var(df$y4, na.rm = TRUE),
                        var(df$y5, na.rm = TRUE),
                        var(df$y6, na.rm = TRUE),
                        var(df$n_x1),
                        var(df$n_x2, na.rm = TRUE),
                        var(df$n_y1),
                        var(df$n_y2, na.rm = TRUE)))

# table 1
kable(tab1, digits = 2) %>%
  kable_classic(html_font = "Arial", full_width = FALSE) %>%
  add_indent(c(5:8))
```

## Supplemental Figure 2.1 - Continuous Exposure

```{r fig2_cont, fig.width=8, fig.height=4, cache.lazy=FALSE}
# now create plot
naimix1 <- ggplot(df, aes(x = n_x1)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.5, alpha = 0.5, color = "grey50") +
  geom_density(adjust = 2) +
  ylab("Density") +
  scale_x_continuous(name = expression(paste("Naimi ", X[1], " (Homoscedastic)")), 
                     limits = c(9, 29), breaks = c(10, 15, 20, 25)) +
  theme

naimix2 <- ggplot(df, aes(x = n_x2)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.5, alpha = 0.5, color = "grey50") +
  geom_density(adjust = 2) +
  ylab("Density") +
  scale_x_continuous(name = expression(paste("Naimi ", X[2], " (Heteroscedastic)")), 
                     limits = c(-0.5, 15), breaks = c(0, 5, 10, 15)) +
  theme

# recreate figure 1
ggarrange(naimix1, naimix2,
          labels = c("A", "B"))
#ggsave("./sim_png/supfig1.1.png")
```

Panel A) Homoscedastic Continuous Exposure, Panel B) Heteroscedastic Continuous Exposure

## Supplemental Figure 2.2 - Continuous Exposure

```{r fig3_cont, fig.width=10, fig.height=4}
# will run ols regression on df
ols_x1_n <- ols(n_x1 ~ + mage + page + mage*page + parity2 + parity3 + parity4 + 
                  parity5, data = df)
ols_x2_n <- ols(n_x2 ~ + mage + page + mage*page + parity2 + parity3 + parity4 + 
                  parity5, data = df) # added 0.001 to avoid -Inf when logging
ols_x2_n_log <- ols(log(n_x2 + 0.001) ~ + mage + page + mage*page + parity2 + parity3 + parity4 + 
                      parity5, data = df) # added 0.001 to avoid -Inf when logging

# linear predictors
preds_x1_n <- predict(ols_x1_n)
preds_x2_n <- predict(ols_x2_n)
preds_x2_n_log <- predict(ols_x2_n_log)

# residuals
res_x1_n <- residuals(ols_x1_n)
res_x2_n <- residuals(ols_x2_n)
res_x2_n_log <- residuals(ols_x2_n_log)

# now plot
x1_plot_n <- ggplot() +
  geom_point(aes(x = preds_x1_n, y = res_x1_n), alpha = 0.01) +
  ylab("Residual") +
  xlab("Linear Predictor") +
  theme

x2_plot_n <- ggplot() +
  geom_point(aes(x = preds_x2_n, y = res_x2_n), alpha = 0.01) +
  ylab("Residual") +
  xlab("Linear Predictor") +
  theme

x2_plot_n_log <- ggplot() +
  geom_point(aes(x = preds_x2_n_log, y = res_x2_n_log), alpha = 0.01) +
  ylab("Residual") +
  xlab("Linear Predictor") +
  theme

# combine
ggarrange(x1_plot_n, x2_plot_n, x2_plot_n_log,
          nrow = 1,
          labels = c("A", "B", "C"))
#ggsave("./sim_png/supfig1.2.png")
```

# Updated Distributions

## Supplemental Figure 2.3 - Maternal Age Distributions

```{r fig1_ma, fig.width=6, fig.height=3, cache.lazy=FALSE}
mage_hist <- df %>%
  ggplot(aes(x = mage)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.1, alpha = 0.5, color = "grey50") +
  geom_density(adjust = 2) +
  ylab("Density") +
  xlab("Normal") +
  labs(caption = paste0("Skew (", round(moments::skewness(df$mage), 3), "), Kurtosis (",
                        round(moments::kurtosis(df$mage), 3), ")")) +
  theme

mage_g_hist <- df %>%
  ggplot(aes(x = mage_g)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.1, alpha = 0.5, color = "grey50") +
  geom_density(adjust = 2) +
  ylab("Density") +
  xlab("Skewed") +
  labs(caption = paste0("Skew (", round(moments::skewness(df$mage_g), 3), "), Kurtosis (",
                        round(moments::kurtosis(df$mage_g), 3), ")")) +
  theme

ggarrange(mage_hist, mage_g_hist,
          labels = c("A", "B"))
#ggsave("./sim_png/supfig1.3.png")
```

Supplemental Figure 3 shows the updated marginal distributions of maternal age (`mage`) and skewed maternal age (`mage_g`). Despite similar means and variances in `mage` and `mage_g`, `mage` is normally distributed whereas `mage_g` is significantly left-skewed.

## Supplemental Figure 2.4 - Exposure-Covariate Correlations

```{r fig1, fig.width=9, fig.height=3, cache.lazy=FALSE}
df %>%
  select(mage, mage_g, x1:x6) %>%
  pivot_longer(x1:x6) %>%
  mutate(mage_fin = ifelse(name %in% c("x1", "x3", "x4", "x6"), mage, mage_g)) %>%
  mutate(name = factor(name,
                       labels = c(expression(paste("A. ", X[1], " - Homoscedastic, Naimi (0.1)")),
                                  expression(paste("B. ", X[2], " - Homoscedastic, Skewed (0.1)")),
                                  expression(paste("C. ", X[3], " - Heterocedastic, Naimi (0.1)")),
                                  expression(paste("D. ", X[4], " - Homoscedastic, Naimi (1)")),
                                  expression(paste("E. ", X[5], " - Homoscedastic, Skewed (1)")),
                                  expression(paste("F. ", X[6], " - Heterocedastic, Naimi (1)"))))) %>%
  ggplot(aes(x = mage_fin, y = value)) +
  facet_wrap(~ name, labeller = "label_parsed") +
  geom_point(alpha = 0.01) +
  ylab("Exposure") +
  xlab("Maternal Age (years)") +
  theme
#ggsave("./sim_png/supfig1.4.png")
```

# Marginal and Conditional Exposure Distributions

## Figure 1 - Marginal and Conditional Exposure Distribution

```{r fig2, fig.width=7, fig.height=7, eval = FALSE}
# Marginal Exposure Distribution

# now create plot
dens_x1 <- ggplot(df, aes(x = x1)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.1, alpha = 0.5, color = "grey50") +
  geom_density(adjust = 2) +
  ylab("Density") +
  scale_x_continuous(name = expression(paste(X[1]))) +
  # labs(caption = paste0("Skew (", round(moments::skewness(df$x1), 3), 
  #       "), Kurtosis (", round(moments::kurtosis(df$x1), 3), ")")) +
  theme + 
  theme(text = element_text(size = 8.5))

dens_x2 <- ggplot(df, aes(x = x2)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.1, alpha = 0.5, color = "grey50") +
  geom_density(adjust = 2) +
  ylab("Density") +
  scale_x_continuous(name = expression(paste(X[2]))) +
  # labs(caption = paste0("Skew (", round(moments::skewness(df$x2), 3), 
  #       "), Kurtosis (", round(moments::kurtosis(df$x2), 3), ")")) +
  theme + 
  theme(text = element_text(size = 8.5))

dens_x3 <- ggplot(df, aes(x = x3)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.1, alpha = 0.5, color = "grey50") +
  geom_density(adjust = 2) +
  ylab("Density") +
  scale_x_continuous(name = expression(paste(X[3]))) +
  # labs(caption = "  ") +
  theme + 
  theme(text = element_text(size = 8.5))

dens_x4 <- ggplot(df, aes(x = x4)) +
  geom_histogram(aes(y = ..density..), binwidth = 1, alpha = 0.5, color = "grey50") +
  #geom_density(adjust = 2) +
  ylab("Density") +
  scale_x_continuous(name = expression(paste(X[4]))) +
  # labs(caption = paste0("Skew (", round(moments::skewness(df$x4), 3), 
  #       "), Kurtosis (", round(moments::kurtosis(df$x4), 3), ")")) +
  theme + 
  theme(text = element_text(size = 8.5))

dens_x5 <- ggplot(df, aes(x = x5)) +
  geom_histogram(aes(y = ..density..), binwidth = 1, alpha = 0.5, color = "grey50") +
  #geom_density(adjust = 2) +
  ylab("Density") +
  scale_x_continuous(name = expression(paste(X[5]))) +
  # labs(caption = paste0("Skew (", round(moments::skewness(df$x5), 3), 
  #       "), Kurtosis (", round(moments::kurtosis(df$x5), 3), ")")) +
  theme + 
  theme(text = element_text(size = 8.5))

dens_x6 <- ggplot(df, aes(x = x6)) +
  geom_histogram(aes(y = ..density..), binwidth = 1, alpha = 0.5, color = "grey50") +
  #geom_density(adjust = 2) +
  ylab("Density") +
  scale_x_continuous(name = expression(paste(X[6]))) +
  # labs(caption = "  ") +
  theme + 
  theme(text = element_text(size = 8.5))

# Conditional Exposure Distribution

# will run ols regression on df
ols_x1 <- ols(x1 ~ + mage + page + mage*page + parity2 + parity3 + parity4 + 
                parity5, data = df)
ols_x2 <- ols(x2 ~ + mage_g + page + mage_g*page + parity2 + parity3 + parity4 + 
                parity5, data = df)
ols_x3 <- ols(x3 ~ + mage + page + mage*page + parity2 + parity3 + parity4 + 
                parity5, data = df)
ols_x4 <- ols(x4 ~ + mage + page + mage*page + parity2 + parity3 + parity4 + 
                parity5, data = df)
ols_x5 <- ols(x5 ~ + mage_g + page + mage_g*page + parity2 + parity3 + parity4 + 
                parity5, data = df)
ols_x6 <- ols(x6 ~ + mage + page + mage*page + parity2 + parity3 + parity4 + 
                parity5, data = df)

# linear predictors
preds_x1 <- predict(ols_x1)
preds_x2 <- predict(ols_x2)
preds_x3 <- predict(ols_x3)
preds_x4 <- predict(ols_x4)
preds_x5 <- predict(ols_x5)
preds_x6 <- predict(ols_x6)

# residuals
res_x1 <- residuals(ols_x1)
res_x2 <- residuals(ols_x2)
res_x3 <- residuals(ols_x3)
res_x4 <- residuals(ols_x4)
res_x5 <- residuals(ols_x5)
res_x6 <- residuals(ols_x6)

# now plot
x1_plot <- ggplot() +
  geom_point(aes(x = preds_x1, y = res_x1), alpha = 0.01) +
  ylab("Residual") +
  scale_x_continuous(name = expression(paste("Linear Predictor (", X[1], ")"))) +
  theme + 
  theme(text = element_text(size = 8.5))

x2_plot <- ggplot() +
  geom_point(aes(x = preds_x2, y = res_x2), alpha = 0.01) +
  ylab("Residual") +
  scale_x_continuous(name = expression(paste("Linear Predictor (", X[2], ")"))) +
  theme + 
  theme(text = element_text(size = 8.5))

x3_plot <- ggplot() +
  geom_point(aes(x = preds_x3, y = res_x3), alpha = 0.01) +
  ylab("Residual") +
  scale_x_continuous(name = expression(paste("Linear Predictor (", X[3], ")"))) +
  theme + 
  theme(text = element_text(size = 8.5))

x4_plot <- ggplot() +
  geom_point(aes(x = preds_x4, y = res_x4), alpha = 0.01) +
  ylab("Residual") +
  scale_x_continuous(name = expression(paste("Linear Predictor (", X[4], ")"))) +
  theme +
  theme(text = element_text(size = 8))

x5_plot <- ggplot() +
  geom_point(aes(x = preds_x5, y = res_x5), alpha = 0.01) +
  ylab("Residual") +
  scale_x_continuous(name = expression(paste("Linear Predictor (", X[5], ")"))) +
  theme +
  theme(text = element_text(size = 8))

x6_plot <- ggplot() +
  geom_point(aes(x = preds_x6, y = res_x6), alpha = 0.01) +
  ylab("Residual") +
  scale_x_continuous(name = expression(paste("Linear Predictor (", X[6], ")"))) +
  theme +
  theme(text = element_text(size = 8))

# combine
ggarrange(dens_x1, x1_plot,
          dens_x2, x2_plot,
          dens_x3, x3_plot,
          dens_x4, x4_plot,
          dens_x5, x5_plot,
          dens_x6, x6_plot,
          labels = c("A)", "B)", "C)", "D)", "E)", "F)",
                     "G)", "H)", "I)", "J)", "K)", "L)"), 
          nrow = 6, ncol = 2,
          font.label = list(size = 10))
# save plot
ggsave("figs/fig1.tiff", width = 7, height = 7)
```


# Stabilized Inverse Probability Weight Assessments

```{r tab2}
# make dataframe that gives the mean IPW weights for each simulation 
# (will then take mean, min, and max of those)
mean_wts <- df %>%
  select(i, x1_ols_wts:x6_olr_wts) %>%
  group_by(i) %>%
  summarise(x1_ols_wts = mean(x1_ols_wts),
            x1_cbgps_wts = mean(x1_cbgps_wts),
            x1_npcbgps_wts = mean(x1_npcbgps_wts),
            x1_qb10_wts = mean(x1_qb10_wts),
            x1_qb15_wts = mean(x1_qb15_wts),
            x1_qb20_wts = mean(x1_qb20_wts),
            x1_olr_wts = mean(x1_olr_wts),
            x2_ols_wts = mean(x2_ols_wts),
            x2_cbgps_wts = mean(x2_cbgps_wts),
            x2_npcbgps_wts = mean(x2_npcbgps_wts),
            x2_qb10_wts = mean(x2_qb10_wts),
            x2_qb15_wts = mean(x2_qb15_wts),
            x2_qb20_wts = mean(x2_qb20_wts),
            x2_olr_wts = mean(x2_olr_wts),
            x3_ols_wts = mean(x3_ols_wts),
            x3_cbgps_wts = mean(x3_cbgps_wts),
            x3_npcbgps_wts = mean(x3_npcbgps_wts),
            x3_qb10_wts = mean(x3_qb10_wts),
            x3_qb15_wts = mean(x3_qb15_wts),
            x3_qb20_wts = mean(x3_qb20_wts),
            x3_olr_wts = mean(x3_olr_wts),
            x4_ols_wts = mean(x4_ols_wts),
            x4_cbgps_wts = mean(x4_cbgps_wts),
            x4_npcbgps_wts = mean(x4_npcbgps_wts),
            x4_olr_wts = mean(x4_olr_wts),
            x5_ols_wts = mean(x5_ols_wts),
            x5_cbgps_wts = mean(x5_cbgps_wts),
            x5_npcbgps_wts = mean(x5_npcbgps_wts),
            x5_olr_wts = mean(x5_olr_wts),
            x6_ols_wts = mean(x6_ols_wts),
            x6_cbgps_wts = mean(x6_cbgps_wts),
            x6_npcbgps_wts = mean(x6_npcbgps_wts),
            x6_olr_wts = mean(x6_olr_wts))

# have to get mean (min, max) of weights from different exposure scenarios
tab2 <- tibble(Method = c("Ordinary least squares",
                          "Covariate balancing generalized propensity score",
                          "Non-parametric covariate balancing generalized propensity score",
                          "Quantile binning categories",
                          "10",
                          "15",
                          "20",
                          "Ordinal logistic regression"),
               `Mean (min, max)` = c(paste0(round(mean(mean_wts$x1_ols_wts), 2), " (",
                                            round(min(mean_wts$x1_ols_wts), 2), ", ",
                                            round(max(mean_wts$x1_ols_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x1_cbgps_wts), 2), " (",
                                            round(min(mean_wts$x1_cbgps_wts), 2), ", ",
                                            round(max(mean_wts$x1_cbgps_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x1_npcbgps_wts), 2), " (",
                                            round(min(mean_wts$x1_npcbgps_wts), 2), ", ",
                                            round(max(mean_wts$x1_npcbgps_wts), 2), ")"),
                                     NA,
                                     paste0(round(mean(mean_wts$x1_qb10_wts), 2), " (",
                                            round(min(mean_wts$x1_qb10_wts), 2), ", ",
                                            round(max(mean_wts$x1_qb10_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x1_qb15_wts), 2), " (",
                                            round(min(mean_wts$x1_qb15_wts), 2), ", ",
                                            round(max(mean_wts$x1_qb15_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x1_qb20_wts), 2), " (",
                                            round(min(mean_wts$x1_qb20_wts), 2), ", ",
                                            round(max(mean_wts$x1_qb20_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x1_olr_wts), 2), " (",
                                            round(min(mean_wts$x1_olr_wts), 2), ", ",
                                            round(max(mean_wts$x1_olr_wts), 2), ")")),
               `Mean (min, max) ` = c(paste0(round(mean(mean_wts$x2_ols_wts), 2), " (",
                                            round(min(mean_wts$x2_ols_wts), 2), ", ",
                                            round(max(mean_wts$x2_ols_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x2_cbgps_wts), 2), " (",
                                            round(min(mean_wts$x2_cbgps_wts), 2), ", ",
                                            round(max(mean_wts$x2_cbgps_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x2_npcbgps_wts), 2), " (",
                                            round(min(mean_wts$x2_npcbgps_wts), 2), ", ",
                                            round(max(mean_wts$x2_npcbgps_wts), 2), ")"),
                                     NA,
                                     paste0(round(mean(mean_wts$x2_qb10_wts), 2), " (",
                                            round(min(mean_wts$x2_qb10_wts), 2), ", ",
                                            round(max(mean_wts$x2_qb10_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x2_qb15_wts), 2), " (",
                                            round(min(mean_wts$x2_qb15_wts), 2), ", ",
                                            round(max(mean_wts$x2_qb15_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x2_qb20_wts), 2), " (",
                                            round(min(mean_wts$x2_qb20_wts), 2), ", ",
                                            round(max(mean_wts$x2_qb20_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x2_olr_wts), 2), " (",
                                            round(min(mean_wts$x2_olr_wts), 2), ", ",
                                            round(max(mean_wts$x2_olr_wts), 2), ")")),
               `Mean (min, max)  ` = c(paste0(round(mean(mean_wts$x3_ols_wts), 2), " (",
                                            round(min(mean_wts$x3_ols_wts), 2), ", ",
                                            round(max(mean_wts$x3_ols_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x3_cbgps_wts), 2), " (",
                                            round(min(mean_wts$x3_cbgps_wts), 2), ", ",
                                            round(max(mean_wts$x3_cbgps_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x3_npcbgps_wts), 2), " (",
                                            round(min(mean_wts$x3_npcbgps_wts), 2), ", ",
                                            round(max(mean_wts$x3_npcbgps_wts), 2), ")"),
                                     NA,
                                     paste0(round(mean(mean_wts$x3_qb10_wts), 2), " (",
                                            round(min(mean_wts$x3_qb10_wts), 2), ", ",
                                            round(max(mean_wts$x3_qb10_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x3_qb15_wts), 2), " (",
                                            round(min(mean_wts$x3_qb15_wts), 2), ", ",
                                            round(max(mean_wts$x3_qb15_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x3_qb20_wts), 2), " (",
                                            round(min(mean_wts$x3_qb20_wts), 2), ", ",
                                            round(max(mean_wts$x3_qb20_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x3_olr_wts), 2), " (",
                                            round(min(mean_wts$x3_olr_wts), 2), ", ",
                                            round(max(mean_wts$x3_olr_wts), 2), ")")),
               `Mean (min, max)   ` = c(paste0(round(mean(df$x4_ols_wts), 2), " (",
                                            round(min(df$x4_ols_wts), 2), ", ",
                                            round(max(df$x4_ols_wts), 2), ")"),
                                     paste0(round(mean(df$x4_cbgps_wts), 2), " (",
                                            round(min(df$x4_cbgps_wts), 2), ", ",
                                            round(max(df$x4_cbgps_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x4_npcbgps_wts), 2), " (",
                                            round(min(mean_wts$x4_npcbgps_wts), 2), ", ",
                                            round(max(mean_wts$x4_npcbgps_wts), 2), ")"),
                                     NA,
                                     NA,
                                     NA,
                                     NA,
                                     paste0(round(mean(df$x4_olr_wts), 2), " (",
                                            round(min(df$x4_olr_wts), 2), ", ",
                                            round(max(df$x4_olr_wts), 2), ")")),
               `Mean (min, max)    ` = c(paste0(round(mean(df$x5_ols_wts), 2), " (",
                                            round(min(df$x5_ols_wts), 2), ", ",
                                            round(max(df$x5_ols_wts), 2), ")"),
                                     paste0(round(mean(df$x5_cbgps_wts), 2), " (",
                                            round(min(df$x5_cbgps_wts), 2), ", ",
                                            round(max(df$x5_cbgps_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x5_npcbgps_wts), 2), " (",
                                            round(min(mean_wts$x5_npcbgps_wts), 2), ", ",
                                            round(max(mean_wts$x5_npcbgps_wts), 2), ")"),
                                     NA,
                                     NA,
                                     NA,
                                     NA,
                                     paste0(round(mean(df$x5_olr_wts), 2), " (",
                                            round(min(df$x5_olr_wts), 2), ", ",
                                            round(max(df$x5_olr_wts), 2), ")")),
               `Mean (min, max)     ` = c(paste0(round(mean(df$x6_ols_wts), 2), " (",
                                            round(min(df$x6_ols_wts), 2), ", ",
                                            round(max(df$x6_ols_wts), 2), ")"),
                                     paste0(round(mean(df$x6_cbgps_wts), 2), " (",
                                            round(min(df$x6_cbgps_wts), 2), ", ",
                                            round(max(df$x6_cbgps_wts), 2), ")"),
                                     paste0(round(mean(mean_wts$x6_npcbgps_wts), 2), " (",
                                            round(min(mean_wts$x6_npcbgps_wts), 2), ", ",
                                            round(max(mean_wts$x6_npcbgps_wts), 2), ")"),
                                     NA,
                                     NA,
                                     NA,
                                     NA,
                                     paste0(round(mean(df$x6_olr_wts), 2), " (",
                                            round(min(df$x6_olr_wts), 2), ", ",
                                            round(max(df$x6_olr_wts), 2), ")"))
               ) 
```

## Covariate Balance

```{r covbal, warning=FALSE, eval = FALSE}
# will need to calculate number of covariates with correlation greated than 0.1 in all exposure scenarios
# start with a function (ignore QB for now)

covbal_func <- function(data){
  # simulation number
  i <- data$i[1]
  
  # start with formulas for different exposures
  x1_formula <- formula(x1 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x2_formula <- formula(x2 ~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + parity5)
  x3_formula <- formula(x3 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x4_formula <- formula(x4 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x5_formula <- formula(x6 ~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + parity5)
  x6_formula <- formula(x6 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  
  # now calculate balance
  bal_tab_x1 <- bal.tab(x1_formula, data = data, 
        weights = list(OLS = "x1_ols_wts",
                       CBGPS = "x1_cbgps_wts",
                       NPCGPS = "x1_npcbgps_wts",
                       CPM = "x1_olr_wts"), 
        stats = c("c"), 
        un = TRUE, thresholds = c(cor = .1))
  bal_tab_x2 <- bal.tab(x2_formula, data = data, 
        weights = list(OLS = "x2_ols_wts",
                       CBGPS = "x2_cbgps_wts",
                       NPCGPS = "x2_npcbgps_wts",
                       CPM = "x2_olr_wts"), 
        stats = c("c"), 
        un = TRUE, thresholds = c(cor = .1))
  bal_tab_x3 <- bal.tab(x3_formula, data = data, 
        weights = list(OLS = "x3_ols_wts",
                       CBGPS = "x3_cbgps_wts",
                       NPCGPS = "x3_npcbgps_wts",
                       CPM = "x3_olr_wts"), 
        stats = c("c"), 
        un = TRUE, thresholds = c(cor = .1))
  bal_tab_x4 <- bal.tab(x4_formula, data = data, 
        weights = list(OLS = "x4_ols_wts",
                       CBGPS = "x4_cbgps_wts",
                       NPCGPS = "x4_npcbgps_wts",
                       CPM = "x4_olr_wts"), 
        stats = c("c"), 
        un = TRUE, thresholds = c(cor = .1))
  bal_tab_x5 <- bal.tab(x5_formula, data = data, 
        weights = list(OLS = "x5_ols_wts",
                       CBGPS = "x5_cbgps_wts",
                       NPCGPS = "x5_npcbgps_wts",
                       CPM = "x5_olr_wts"), 
        stats = c("c"), 
        un = TRUE, thresholds = c(cor = .1))
  bal_tab_x6 <- bal.tab(x6_formula, data = data, 
        weights = list(OLS = "x6_ols_wts",
                       CBGPS = "x6_cbgps_wts",
                       NPCGPS = "x6_npcbgps_wts",
                       CPM = "x6_olr_wts"), 
        stats = c("c"), 
        un = TRUE, thresholds = c(cor = .1))
  
  # now calculate quantile binning correlations
  
  # qb10
  x1_qb10form <- formula(x1_qb10 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x2_qb10form <- formula(x2_qb10 ~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + parity5)
  x3_qb10form <- formula(x3_qb10 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  
  bal_tab_x1_qb10 <- bal.tab(x1_qb10form, data = data, weights = "x1_qb10_wts", stats = c("c"), 
                             un = TRUE, thresholds = c(cor = .1))
  bal_tab_x2_qb10 <- bal.tab(x2_qb10form, data = data, weights = "x2_qb10_wts", stats = c("c"), 
                             un = TRUE, thresholds = c(cor = .1))
  bal_tab_x3_qb10 <- bal.tab(x3_qb10form, data = data, weights = "x3_qb10_wts", stats = c("c"), 
                             un = TRUE, thresholds = c(cor = .1))
  
  # qb15
  x1_qb15form <- formula(x1_qb15 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x2_qb15form <- formula(x2_qb15 ~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + parity5)
  x3_qb15form <- formula(x3_qb15 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  
  bal_tab_x1_qb15 <- bal.tab(x1_qb15form, data = data, weights = "x1_qb15_wts", stats = c("c"), 
                             un = TRUE, thresholds = c(cor = .1))
  bal_tab_x2_qb15 <- bal.tab(x2_qb15form, data = data, weights = "x2_qb15_wts", stats = c("c"), 
                             un = TRUE, thresholds = c(cor = .1))
  bal_tab_x3_qb15 <- bal.tab(x3_qb15form, data = data, weights = "x3_qb15_wts", stats = c("c"), 
                             un = TRUE, thresholds = c(cor = .1))
  
  # qb20
  x1_qb20form <- formula(x1_qb20 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  x2_qb20form <- formula(x2_qb20 ~ mage_g + page + mage_g*page + parity2 + parity3 + parity4 + parity5)
  x3_qb20form <- formula(x3_qb20 ~ mage + page + mage*page + parity2 + parity3 + parity4 + parity5)
  
  bal_tab_x1_qb20 <- bal.tab(x1_qb20form, data = data, weights = "x1_qb20_wts", stats = c("c"), 
                             un = TRUE, thresholds = c(cor = .1))
  bal_tab_x2_qb20 <- bal.tab(x2_qb20form, data = data, weights = "x2_qb20_wts", stats = c("c"), 
                             un = TRUE, thresholds = c(cor = .1))
  bal_tab_x3_qb20 <- bal.tab(x3_qb20form, data = data, weights = "x3_qb20_wts", stats = c("c"), 
                             un = TRUE, thresholds = c(cor = .1))
  
  # now combine into output dataframe
  data_frame(i, 
             x1_uw = sum(bal_tab_x1$Balance$Corr.Un < 0.1),
             x1_ols = bal_tab_x1$Balanced.correlations[2, 1],
             x1_cbgps = bal_tab_x1$Balanced.correlations[2, 2],
             x1_npcbgps = bal_tab_x1$Balanced.correlations[2, 3],
             x1_qb10 = bal_tab_x1_qb10$Balanced.correlations[2, 1],
             x1_qb15 = bal_tab_x1_qb15$Balanced.correlations[2, 1],
             x1_qb20 = bal_tab_x1_qb20$Balanced.correlations[2, 1],
             x1_olr = bal_tab_x1$Balanced.correlations[2, 4], 
             x2_uw = sum(bal_tab_x2$Balance$Corr.Un < 0.1),
             x2_ols = bal_tab_x2$Balanced.correlations[2, 1],
             x2_cbgps = bal_tab_x2$Balanced.correlations[2, 2],
             x2_npcbgps = bal_tab_x2$Balanced.correlations[2, 3],
             x2_qb10 = bal_tab_x2_qb10$Balanced.correlations[2, 1],
             x2_qb15 = bal_tab_x2_qb15$Balanced.correlations[2, 1],
             x2_qb20 = bal_tab_x2_qb20$Balanced.correlations[2, 1],
             x2_olr = bal_tab_x2$Balanced.correlations[2, 4], 
             x3_uw = sum(bal_tab_x3$Balance$Corr.Un < 0.1),
             x3_ols = bal_tab_x3$Balanced.correlations[2, 1],
             x3_cbgps = bal_tab_x3$Balanced.correlations[2, 2],
             x3_npcbgps = bal_tab_x3$Balanced.correlations[2, 3],
             x3_qb10 = bal_tab_x3_qb10$Balanced.correlations[2, 1],
             x3_qb15 = bal_tab_x3_qb15$Balanced.correlations[2, 1],
             x3_qb20 = bal_tab_x3_qb20$Balanced.correlations[2, 1],
             x3_olr = bal_tab_x3$Balanced.correlations[2, 4], 
             x4_uw = sum(bal_tab_x4$Balance$Corr.Un < 0.1),
             x4_ols = bal_tab_x4$Balanced.correlations[2, 1],
             x4_cbgps = bal_tab_x4$Balanced.correlations[2, 2],
             x4_npcbgps = bal_tab_x4$Balanced.correlations[2, 3],
             x4_qb10 = NA,
             x4_qb15 = NA,
             x4_qb20 = NA,
             x4_olr = bal_tab_x4$Balanced.correlations[2, 4], 
             x5_uw = sum(bal_tab_x5$Balance$Corr.Un < 0.1),
             x5_ols = bal_tab_x5$Balanced.correlations[2, 1],
             x5_cbgps = bal_tab_x5$Balanced.correlations[2, 2],
             x5_npcbgps = bal_tab_x5$Balanced.correlations[2, 3],
             x5_qb10 = NA,
             x5_qb15 = NA,
             x5_qb20 = NA,
             x5_olr = bal_tab_x5$Balanced.correlations[2, 4], 
             x6_uw = sum(bal_tab_x6$Balance$Corr.Un < 0.1),
             x6_ols = bal_tab_x6$Balanced.correlations[2, 1],
             x6_cbgps = bal_tab_x6$Balanced.correlations[2, 2],
             x6_npcbgps = bal_tab_x6$Balanced.correlations[2, 3],
             x6_qb10 = NA,
             x6_qb15 = NA,
             x6_qb20 = NA,
             x6_olr = bal_tab_x6$Balanced.correlations[2, 4])
}

# # get covariate balance across all simulations
# covbal <- map_df(sims[1:10], ~ covbal_func(.x))

# run in parallel with furrr
plan(multisession, workers = 7)
covbal <- future_map_dfr(sims, ~ covbal_func(.x))

# save
Save(covbal)
```


```{r covbal_tab}
# load covbal
Load(covbal)

# now make table of mean squared error, which is the mean of the squared biases (or errors)
covbal_tab <- tibble(Method = c("Unweighted",
                                "Ordinary least squares",
                          "Covariate balancing generalized propensity score",
                          "Non-parametric covariate balancing generalized propensity score",
                          "Quantile binning categories",
                          "10",
                          "15",
                          "20",
                          "Ordinal logistic regression"),
               `Mean (min, max)` = c(paste0(round(mean(covbal$x1_uw), 2), " (",
                                            min(covbal$x1_uw), ", ",
                                            max(covbal$x1_uw), ")"),
                                     paste0(round(mean(covbal$x1_ols), 2), " (",
                                            min(covbal$x1_ols), ", ",
                                            max(covbal$x1_ols), ")"),
                                     paste0(round(mean(covbal$x1_cbgps), 2), " (",
                                            min(covbal$x1_cbgps), ", ",
                                            max(covbal$x1_cbgps), ")"),
                                     paste0(round(mean(covbal$x1_npcbgps), 2), " (",
                                            min(covbal$x1_npcbgps), ", ",
                                            max(covbal$x1_npcbgps), ")"),
                                     NA,
                                     paste0(round(mean(covbal$x1_qb10), 2), " (",
                                            min(covbal$x1_qb10), ", ",
                                            max(covbal$x1_qb10), ")"),
                                     paste0(round(mean(covbal$x1_qb15), 2), " (",
                                            min(covbal$x1_qb15), ", ",
                                            max(covbal$x1_qb15), ")"),
                                     paste0(round(mean(covbal$x1_qb20), 2), " (",
                                            min(covbal$x1_qb20), ", ",
                                            max(covbal$x1_qb20), ")"),
                                     paste0(round(mean(covbal$x1_olr), 2), " (",
                                            min(covbal$x1_olr), ", ",
                                            max(covbal$x1_olr), ")")),
               `Mean (min, max) ` = c(paste0(round(mean(covbal$x2_uw), 2), " (",
                                            min(covbal$x2_uw), ", ",
                                            max(covbal$x2_uw), ")"),
                                     paste0(round(mean(covbal$x2_ols), 2), " (",
                                            min(covbal$x2_ols), ", ",
                                            max(covbal$x2_ols), ")"),
                                     paste0(round(mean(covbal$x2_cbgps), 2), " (",
                                            min(covbal$x2_cbgps), ", ",
                                            max(covbal$x2_cbgps), ")"),
                                     paste0(round(mean(covbal$x2_npcbgps), 2), " (",
                                            min(covbal$x2_npcbgps), ", ",
                                            max(covbal$x2_npcbgps), ")"),
                                     NA,
                                     paste0(round(mean(covbal$x2_qb10), 2), " (",
                                            min(covbal$x2_qb10), ", ",
                                            max(covbal$x2_qb10), ")"),
                                     paste0(round(mean(covbal$x2_qb15), 2), " (",
                                            min(covbal$x2_qb15), ", ",
                                            max(covbal$x2_qb15), ")"),
                                     paste0(round(mean(covbal$x2_qb20), 2), " (",
                                            min(covbal$x2_qb20), ", ",
                                            max(covbal$x2_qb20), ")"),
                                     paste0(round(mean(covbal$x2_olr), 2), " (",
                                            min(covbal$x2_olr), ", ",
                                            max(covbal$x2_olr), ")")),
               `Mean (min, max)  ` = c(paste0(round(mean(covbal$x3_uw), 2), " (",
                                            min(covbal$x3_uw), ", ",
                                            max(covbal$x3_uw), ")"),
                                     paste0(round(mean(covbal$x3_ols), 2), " (",
                                            min(covbal$x3_ols), ", ",
                                            max(covbal$x3_ols), ")"),
                                     paste0(round(mean(covbal$x3_cbgps), 2), " (",
                                            min(covbal$x3_cbgps), ", ",
                                            max(covbal$x3_cbgps), ")"),
                                     paste0(round(mean(covbal$x3_npcbgps), 2), " (",
                                            min(covbal$x3_npcbgps), ", ",
                                            max(covbal$x3_npcbgps), ")"),
                                     NA,
                                     paste0(round(mean(covbal$x3_qb10), 2), " (",
                                            min(covbal$x3_qb10), ", ",
                                            max(covbal$x3_qb10), ")"),
                                     paste0(round(mean(covbal$x3_qb15), 2), " (",
                                            min(covbal$x3_qb15), ", ",
                                            max(covbal$x3_qb15), ")"),
                                     paste0(round(mean(covbal$x3_qb20), 2), " (",
                                            min(covbal$x3_qb20), ", ",
                                            max(covbal$x3_qb20), ")"),
                                     paste0(round(mean(covbal$x3_olr), 2), " (",
                                            min(covbal$x3_olr), ", ",
                                            max(covbal$x3_olr), ")")),
               `Mean (min, max)   ` = c(paste0(round(mean(covbal$x4_uw), 2), " (",
                                            min(covbal$x4_uw), ", ",
                                            max(covbal$x4_uw), ")"),
                                        paste0(round(mean(covbal$x4_ols), 2), " (",
                                            min(covbal$x4_ols), ", ",
                                            max(covbal$x4_ols), ")"),
                                     paste0(round(mean(covbal$x4_cbgps), 2), " (",
                                            min(covbal$x4_cbgps), ", ",
                                            max(covbal$x4_cbgps), ")"),
                                     paste0(round(mean(covbal$x4_npcbgps), 2), " (",
                                            min(covbal$x4_npcbgps), ", ",
                                            max(covbal$x4_npcbgps), ")"),
                                     NA,
                                     NA,
                                     NA,
                                     NA,
                                     paste0(round(mean(covbal$x4_olr), 2), " (",
                                            min(covbal$x4_olr), ", ",
                                            max(covbal$x4_olr), ")")),
               `Mean (min, max)    ` = c(paste0(round(mean(covbal$x5_uw), 2), " (",
                                            min(covbal$x5_uw), ", ",
                                            max(covbal$x5_uw), ")"),
                                         paste0(round(mean(covbal$x5_ols), 2), " (",
                                            min(covbal$x5_ols), ", ",
                                            max(covbal$x5_ols), ")"),
                                     paste0(round(mean(covbal$x5_cbgps), 2), " (",
                                            min(covbal$x5_cbgps), ", ",
                                            max(covbal$x5_cbgps), ")"),
                                     paste0(round(mean(covbal$x5_npcbgps), 2), " (",
                                            min(covbal$x5_npcbgps), ", ",
                                            max(covbal$x5_npcbgps), ")"),
                                     NA,
                                     NA,
                                     NA,
                                     NA,
                                     paste0(round(mean(covbal$x5_olr), 2), " (",
                                            min(covbal$x5_olr), ", ",
                                            max(covbal$x5_olr), ")")),
               `Mean (min, max)     ` = c(paste0(round(mean(covbal$x6_uw), 2), " (",
                                            min(covbal$x6_uw), ", ",
                                            max(covbal$x6_uw), ")"),
                                          paste0(round(mean(covbal$x6_ols), 2), " (",
                                            min(covbal$x6_ols), ", ",
                                            max(covbal$x6_ols), ")"),
                                     paste0(round(mean(covbal$x6_cbgps), 2), " (",
                                            min(covbal$x6_cbgps), ", ",
                                            max(covbal$x6_cbgps), ")"),
                                     paste0(round(mean(covbal$x6_npcbgps), 2), " (",
                                            min(covbal$x6_npcbgps), ", ",
                                            max(covbal$x6_npcbgps), ")"),
                                     NA,
                                     NA,
                                     NA,
                                     NA,
                                     paste0(round(mean(covbal$x6_olr), 2), " (",
                                            min(covbal$x6_olr), ", ",
                                            max(covbal$x6_olr), ")"))
               ) 
```

## Table 2 - Inverse Probability Weight and Covariate Balance Distributions [Mean (Min, Max) Version]

```{r fin_tab1, eval = FALSE}
fin_tab1 <- tibble(Method = c("Unweighted",
                              "Stabilized weight",
                              "Unbalanced covariates",
                          "Ordinary least squares",
                          "Stabilized weight",
                              "Unbalanced covariates",
                          "Covariate balancing generalized propensity score",
                          "Stabilized weight",
                              "Unbalanced covariates",
                          "Non-parametric covariate balancing generalized propensity score",
                          "Stabilized weight",
                              "Unbalanced covariates",
                          "Quantile binning categories",
                          "10",
                          "Stabilized weight",
                              "Unbalanced covariates",
                          "15",
                          "Stabilized weight",
                              "Unbalanced covariates",
                          "20",
                          "Stabilized weight",
                              "Unbalanced covariates",
                          "Ordinal logistic regression",
                          "Stabilized weight",
                              "Unbalanced covariates"),
                   `Mean (min, max)` = c(NA, NA, covbal_tab[1, 2],
                                         NA, tab2[1, 2], covbal_tab[2, 2],
                                         NA, tab2[2, 2], covbal_tab[3, 2],
                                         NA, tab2[3, 2], covbal_tab[4, 2],
                                         NA,
                                         NA, tab2[5, 2], covbal_tab[6, 2],
                                         NA, tab2[6, 2], covbal_tab[7, 2],
                                         NA, tab2[7, 2], covbal_tab[8, 2],
                                         NA, tab2[8, 2], covbal_tab[9, 2]),
                   `Mean (min, max)   ` = c(NA, NA, covbal_tab[1, 5],
                                         NA, tab2[1, 5], covbal_tab[2, 5],
                                         NA, tab2[2, 5], covbal_tab[3, 5],
                                         NA, tab2[3, 5], covbal_tab[4, 5],
                                         NA,
                                         NA, tab2[5, 5], covbal_tab[6, 5],
                                         NA, tab2[6, 5], covbal_tab[7, 5],
                                         NA, tab2[7, 5], covbal_tab[8, 5],
                                         NA, tab2[8, 5], covbal_tab[9, 5]),
                   `Mean (min, max) ` = c(NA, NA, covbal_tab[1, 3],
                                         NA, tab2[1, 3], covbal_tab[2, 3],
                                         NA, tab2[2, 3], covbal_tab[3, 3],
                                         NA, tab2[3, 3], covbal_tab[4, 3],
                                         NA,
                                         NA, tab2[5, 3], covbal_tab[6, 3],
                                         NA, tab2[6, 3], covbal_tab[7, 3],
                                         NA, tab2[7, 3], covbal_tab[8, 3],
                                         NA, tab2[8, 3], covbal_tab[9, 3]),
                   `Mean (min, max)    `  = c(NA, NA, covbal_tab[1, 6],
                                         NA, tab2[1, 6], covbal_tab[2, 6],
                                         NA, tab2[2, 6], covbal_tab[3, 6],
                                         NA, tab2[3, 6], covbal_tab[4, 6],
                                         NA,
                                         NA, tab2[5, 6], covbal_tab[6, 6],
                                         NA, tab2[6, 6], covbal_tab[7, 6],
                                         NA, tab2[7, 6], covbal_tab[8, 6],
                                         NA, tab2[8, 6], covbal_tab[9, 6]),
                   `Mean (min, max)  ` = c(NA, NA, covbal_tab[1, 4],
                                         NA, tab2[1, 4], covbal_tab[2, 4],
                                         NA, tab2[2, 4], covbal_tab[3, 4],
                                         NA, tab2[3, 4], covbal_tab[4, 4],
                                         NA,
                                         NA, tab2[5, 4], covbal_tab[6, 4],
                                         NA, tab2[6, 4], covbal_tab[7, 4],
                                         NA, tab2[7, 4], covbal_tab[8, 4],
                                         NA, tab2[8, 4], covbal_tab[9, 4]),
                   `Mean (min, max)     `  = c(NA, NA, covbal_tab[1, 7],
                                         NA, tab2[1, 7], covbal_tab[2, 7],
                                         NA, tab2[2, 7], covbal_tab[3, 7],
                                         NA, tab2[3, 7], covbal_tab[4, 7],
                                         NA,
                                         NA, tab2[5, 7], covbal_tab[6, 7],
                                         NA, tab2[6, 7], covbal_tab[7, 7],
                                         NA, tab2[7, 7], covbal_tab[8, 7],
                                         NA, tab2[8, 7], covbal_tab[9, 7]))

kable(fin_tab1) %>%
  kable_classic(html_font = "Arial", full_width = FALSE) %>%
  add_header_above(c("Exposure", "X1" = 1, "X4" = 1, "X2" = 1, "X5" = 1, 
                     "X3" = 1, "X6" = 1), bold = TRUE) %>%
  add_header_above(c("Marginally", "Normal" = 2, "Non-Normal" = 2, 
                     "Non-Normal" = 2), bold = TRUE) %>%
  add_header_above(c("Conditionally", "Normal" = 2, "Normal" = 2, 
                     "Non-Normal" = 2), bold = TRUE)  %>%
  add_indent(c(2:3, 5:6, 8:9, 11:12, 14:22, 24:25)) %>%
  add_indent(c(2:3, 5:6, 8:9, 11:12, 15:16, 18:19, 21:22, 24:25))
```

# Assessment of Bias

### Calculating Bias and Mean Squared Error

```{r bias_mse, warning=FALSE, eval=FALSE}
# will need to calculate all weights using x1 and x2 for each 
  # simulated dataset with weighted lrm models
# then calculate bias for exposure coefficient versus truth

# create deciles quantiles for each Austin approach
x1_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x1, .x))

x2_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x2, .x))

x3_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x3, .x))

x4_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x4, .x))

x5_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x5, .x))

x6_quants <- map_dbl(seq(0.1, 0.9, 0.1), ~ quantile(df$x6, .x))

# function to get list of biases via msm approach and Austin approaches
bias_func <- function(data){
  # simulation number
  i <- data$i[1]

  # bias via the Marginal Structural Model Approach
  
  # generate weighted models
  # unweighted comparison
  x1_uw <- lrm(y1 ~ x1, data = data)
  x2_uw <- lrm(y2 ~ x2, data = data)
  x3_uw <- lrm(y3 ~ x3, data = data)
  x4_uw  <- lrm(y4 ~ x4, data = data)
  x5_uw  <- lrm(y5 ~ x5, data = data)
  x6_uw  <- lrm(y6 ~ x6, data = data)
  
  # ols
  d_ols_x1 <- svydesign(~1, weights = data$x1_ols_wts, data = data)
  x1_ols <- svyglm(y1 ~ x1, design = d_ols_x1, family = binomial)
  d_ols_x2 <- svydesign(~1, weights = data$x2_ols_wts, data = data)
  x2_ols <- svyglm(y2 ~ x2, design = d_ols_x2, family = binomial)
  d_ols_x3 <- svydesign(~1, weights = data$x3_ols_wts, data = data)
  x3_ols <- svyglm(y3 ~ x3, design = d_ols_x3, family = binomial)
  d_ols_x4 <- svydesign(~1, weights = data$x4_ols_wts, data = data)
  x4_ols <- svyglm(y4 ~ x4, design = d_ols_x4, family = binomial)
  d_ols_x5 <- svydesign(~1, weights = data$x5_ols_wts, data = data)
  x5_ols <- svyglm(y5 ~ x5, design = d_ols_x5, family = binomial)
  d_ols_x6 <- svydesign(~1, weights = data$x6_ols_wts, data = data)
  x6_ols <- svyglm(y6 ~ x6, design = d_ols_x6, family = binomial)
  
  # cbgps
  d_cbgps_x1 <- svydesign(~1, weights = data$x1_cbgps_wts, data = data)
  x1_cbgps <- svyglm(y1 ~ x1, design = d_cbgps_x1, family = binomial)
  d_cbgps_x2 <- svydesign(~1, weights = data$x2_cbgps_wts, data = data)
  x2_cbgps <- svyglm(y2 ~ x2, design = d_cbgps_x2, family = binomial)
  d_cbgps_x3 <- svydesign(~1, weights = data$x3_cbgps_wts, data = data)
  x3_cbgps <- svyglm(y3 ~ x3, design = d_cbgps_x3, family = binomial)
  d_cbgps_x4 <- svydesign(~1, weights = data$x4_cbgps_wts, data = data)
  x4_cbgps <- svyglm(y4 ~ x4, design = d_cbgps_x4, family = binomial)
  d_cbgps_x5 <- svydesign(~1, weights = data$x5_cbgps_wts, data = data)
  x5_cbgps <- svyglm(y5 ~ x5, design = d_cbgps_x5, family = binomial)
  d_cbgps_x6 <- svydesign(~1, weights = data$x6_cbgps_wts, data = data)
  x6_cbgps <- svyglm(y6 ~ x6, design = d_cbgps_x6, family = binomial)
  
  # npcbgps
  d_npcbgps_x1 <- svydesign(~1, weights = data$x1_npcbgps_wts, data = data)
  x1_npcbgps <- svyglm(y1 ~ x1, design = d_npcbgps_x1, family = binomial)
  d_npcbgps_x2 <- svydesign(~1, weights = data$x2_npcbgps_wts, data = data)
  x2_npcbgps <- svyglm(y2 ~ x2, design = d_npcbgps_x2, family = binomial)
  d_npcbgps_x3 <- svydesign(~1, weights = data$x3_npcbgps_wts, data = data)
  x3_npcbgps <- svyglm(y3 ~ x3, design = d_npcbgps_x3, family = binomial)
  d_npcbgps_x4 <- svydesign(~1, weights = data$x4_npcbgps_wts, data = data)
  x4_npcbgps <- svyglm(y4 ~ x4, design = d_npcbgps_x4, family = binomial)
  d_npcbgps_x5 <- svydesign(~1, weights = data$x5_npcbgps_wts, data = data)
  x5_npcbgps <- svyglm(y5 ~ x5, design = d_npcbgps_x5, family = binomial)
  d_npcbgps_x6 <- svydesign(~1, weights = data$x6_npcbgps_wts, data = data)
  x6_npcbgps <- svyglm(y6 ~ x6, design = d_npcbgps_x6, family = binomial)
  
  # qb10
  d_qb10_x1 <- svydesign(~1, weights = data$x1_qb10_wts, data = data)
  x1_qb10 <- svyglm(y1 ~ x1, design = d_qb10_x1, family = binomial)
  d_qb10_x2 <- svydesign(~1, weights = data$x2_qb10_wts, data = data)
  x2_qb10 <- svyglm(y2 ~ x2, design = d_qb10_x2, family = binomial)
  d_qb10_x3 <- svydesign(~1, weights = data$x3_qb10_wts, data = data)
  x3_qb10 <- svyglm(y3 ~ x3, design = d_qb10_x3, family = binomial)
  
  # qb15
  d_qb15_x1 <- svydesign(~1, weights = data$x1_qb15_wts, data = data)
  x1_qb15 <- svyglm(y1 ~ x1, design = d_qb15_x1, family = binomial)
  d_qb15_x2 <- svydesign(~1, weights = data$x2_qb15_wts, data = data)
  x2_qb15 <- svyglm(y2 ~ x2, design = d_qb15_x2, family = binomial)
  d_qb15_x3 <- svydesign(~1, weights = data$x3_qb15_wts, data = data)
  x3_qb15 <- svyglm(y3 ~ x3, design = d_qb15_x3, family = binomial)
  
  # qb20
  d_qb20_x1 <- svydesign(~1, weights = data$x1_qb20_wts, data = data)
  x1_qb20 <- svyglm(y1 ~ x1, design = d_qb20_x1, family = binomial)
  d_qb20_x2 <- svydesign(~1, weights = data$x2_qb20_wts, data = data)
  x2_qb20 <- svyglm(y2 ~ x2, design = d_qb20_x2, family = binomial)
  d_qb20_x3 <- svydesign(~1, weights = data$x3_qb20_wts, data = data)
  x3_qb20 <- svyglm(y3 ~ x3, design = d_qb20_x3, family = binomial)
  
  # olr
  d_olr_x1 <- svydesign(~1, weights = data$x1_olr_wts, data = data)
  x1_olr <- svyglm(y1 ~ x1, design = d_olr_x1, family = binomial)
  d_olr_x2 <- svydesign(~1, weights = data$x2_olr_wts, data = data)
  x2_olr <- svyglm(y2 ~ x2, design = d_olr_x2, family = binomial)
  d_olr_x3 <- svydesign(~1, weights = data$x3_olr_wts, data = data)
  x3_olr <- svyglm(y3 ~ x3, design = d_olr_x3, family = binomial)
  d_olr_x4 <- svydesign(~1, weights = data$x4_olr_wts, data = data)
  x4_olr <- svyglm(y4 ~ x4, design = d_olr_x4, family = binomial)
  d_olr_x5 <- svydesign(~1, weights = data$x5_olr_wts, data = data)
  x5_olr <- svyglm(y5 ~ x5, design = d_olr_x5, family = binomial)
  d_olr_x6 <- svydesign(~1, weights = data$x6_olr_wts, data = data)
  x6_olr <- svyglm(y6 ~ x6, design = d_olr_x6, family = binomial)

  # bias via the Marginal Structural Model Approach
  
  # unweighted bias
  x1_uw_bias <- true_x1 - x1_uw$coefficient[2]
  x2_uw_bias <- true_x2 - x2_uw$coefficient[2]
  x3_uw_bias <- true_x3 - x3_uw$coefficient[2]
  x4_uw_bias <- true_x4 - x4_uw$coefficient[2]
  x5_uw_bias <- true_x5 - x5_uw$coefficient[2]
  x6_uw_bias <- true_x6 - x6_uw$coefficient[2]
  
  # unweighted se
  x1_uw_se <- sqrt(x1_uw$var[2,2])
  x2_uw_se <- sqrt(x2_uw$var[2,2])
  x3_uw_se <- sqrt(x3_uw$var[2,2])
  x4_uw_se <- sqrt(x4_uw$var[2,2])
  x5_uw_se <- sqrt(x5_uw$var[2,2])
  x6_uw_se <- sqrt(x6_uw$var[2,2])
  
  # unweighted coverage
  x1_uw_cov <- (true_x1 > (x1_uw$coefficient[2] - (1.96 * x1_uw_se))) & 
    (true_x1 < (x1_uw$coefficient[2] + (1.96 * x1_uw_se)))
  x2_uw_cov <- (true_x2 > (x2_uw$coefficient[2] - (1.96 * x2_uw_se))) & 
    (true_x2 < (x2_uw$coefficient[2] + (1.96 * x2_uw_se)))
  x3_uw_cov <- (true_x3 > (x3_uw$coefficient[2] - (1.96 * x3_uw_se))) & 
    (true_x3 < (x3_uw$coefficient[2] + (1.96 * x3_uw_se)))
  x4_uw_cov <- (true_x4 > (x4_uw$coefficient[2] - (1.96 * x4_uw_se))) & 
    (true_x4 < (x4_uw$coefficient[2] + (1.96 * x4_uw_se)))
  x5_uw_cov <- (true_x5 > (x5_uw$coefficient[2] - (1.96 * x5_uw_se))) & 
    (true_x5 < (x5_uw$coefficient[2] + (1.96 * x5_uw_se)))
  x6_uw_cov <- (true_x6 > (x6_uw$coefficient[2] - (1.96 * x6_uw_se))) & 
    (true_x6 < (x6_uw$coefficient[2] + (1.96 * x6_uw_se)))
  
  # ols
  x1_ols_bias <- true_x1 - x1_ols$coefficient[2]
  x2_ols_bias <- true_x2 - x2_ols$coefficient[2]
  x3_ols_bias <- true_x3 - x3_ols$coefficient[2]
  x4_ols_bias <- true_x4 - x4_ols$coefficient[2]
  x5_ols_bias <- true_x5 - x5_ols$coefficient[2]
  x6_ols_bias <- true_x6 - x6_ols$coefficient[2]
  
  # ols se
  x1_ols_se <- sqrt(x1_ols$cov.unscaled[2,2])
  x2_ols_se <- sqrt(x2_ols$cov.unscaled[2,2])
  x3_ols_se <- sqrt(x3_ols$cov.unscaled[2,2])
  x4_ols_se <- sqrt(x4_ols$cov.unscaled[2,2])
  x5_ols_se <- sqrt(x5_ols$cov.unscaled[2,2])
  x6_ols_se <- sqrt(x6_ols$cov.unscaled[2,2])
  
  # ols coverage
  x1_ols_cov <- (true_x1 > (x1_ols$coefficient[2] - (1.96 * x1_ols_se))) & 
    (true_x1 < (x1_ols$coefficient[2] + (1.96 * x1_ols_se)))
  x2_ols_cov <- (true_x2 > (x2_ols$coefficient[2] - (1.96 * x2_ols_se))) & 
    (true_x2 < (x2_ols$coefficient[2] + (1.96 * x2_ols_se)))
  x3_ols_cov <- (true_x3 > (x3_ols$coefficient[2] - (1.96 * x3_ols_se))) & 
    (true_x3 < (x3_ols$coefficient[2] + (1.96 * x3_ols_se)))
  x4_ols_cov <- (true_x4 > (x4_ols$coefficient[2] - (1.96 * x4_ols_se))) & 
    (true_x4 < (x4_ols$coefficient[2] + (1.96 * x4_ols_se)))
  x5_ols_cov <- (true_x5 > (x5_ols$coefficient[2] - (1.96 * x5_ols_se))) & 
    (true_x5 < (x5_ols$coefficient[2] + (1.96 * x5_ols_se)))
  x6_ols_cov <- (true_x6 > (x6_ols$coefficient[2] - (1.96 * x6_ols_se))) & 
    (true_x6 < (x6_ols$coefficient[2] + (1.96 * x6_ols_se)))
  
  # cbgps
  x1_cbgps_bias <- true_x1 - x1_cbgps$coefficient[2]
  x2_cbgps_bias <- true_x2 - x2_cbgps$coefficient[2]
  x3_cbgps_bias <- true_x3 - x3_cbgps$coefficient[2]
  x4_cbgps_bias <- true_x4 - x4_cbgps$coefficient[2]
  x5_cbgps_bias <- true_x5 - x5_cbgps$coefficient[2]
  x6_cbgps_bias <- true_x6 - x6_cbgps$coefficient[2]
  
  # cbgps se
  x1_cbgps_se <- sqrt(x1_cbgps$cov.unscaled[2,2])
  x2_cbgps_se <- sqrt(x2_cbgps$cov.unscaled[2,2])
  x3_cbgps_se <- sqrt(x3_cbgps$cov.unscaled[2,2])
  x4_cbgps_se <- sqrt(x4_cbgps$cov.unscaled[2,2])
  x5_cbgps_se <- sqrt(x5_cbgps$cov.unscaled[2,2])
  x6_cbgps_se <- sqrt(x6_cbgps$cov.unscaled[2,2])
  
  # cbgps coverage
  x1_cbgps_cov <- (true_x1 > (x1_cbgps$coefficient[2] - (1.96 * x1_cbgps_se))) & 
    (true_x1 < (x1_cbgps$coefficient[2] + (1.96 * x1_cbgps_se)))
  x2_cbgps_cov <- (true_x2 > (x2_cbgps$coefficient[2] - (1.96 * x2_cbgps_se))) & 
    (true_x2 < (x2_cbgps$coefficient[2] + (1.96 * x2_cbgps_se)))
  x3_cbgps_cov <- (true_x3 > (x3_cbgps$coefficient[2] - (1.96 * x3_cbgps_se))) & 
    (true_x3 < (x3_cbgps$coefficient[2] + (1.96 * x3_cbgps_se)))
  x4_cbgps_cov <- (true_x4 > (x4_cbgps$coefficient[2] - (1.96 * x4_cbgps_se))) & 
    (true_x4 < (x4_cbgps$coefficient[2] + (1.96 * x4_cbgps_se)))
  x5_cbgps_cov <- (true_x5 > (x5_cbgps$coefficient[2] - (1.96 * x5_cbgps_se))) & 
    (true_x5 < (x5_cbgps$coefficient[2] + (1.96 * x5_cbgps_se)))
  x6_cbgps_cov <- (true_x6 > (x6_cbgps$coefficient[2] - (1.96 * x6_cbgps_se))) & 
    (true_x6 < (x6_cbgps$coefficient[2] + (1.96 * x6_cbgps_se)))
  
  # npcbgps
  x1_npcbgps_bias <- true_x1 - x1_npcbgps$coefficient[2]
  x2_npcbgps_bias <- true_x2 - x2_npcbgps$coefficient[2]
  x3_npcbgps_bias <- true_x3 - x3_npcbgps$coefficient[2]
  x4_npcbgps_bias <- true_x4 - x4_npcbgps$coefficient[2]
  x5_npcbgps_bias <- true_x5 - x5_npcbgps$coefficient[2]
  x6_npcbgps_bias <- true_x6 - x6_npcbgps$coefficient[2]
  
  # npcbgps se
  x1_npcbgps_se <- sqrt(x1_npcbgps$cov.unscaled[2,2])
  x2_npcbgps_se <- sqrt(x2_npcbgps$cov.unscaled[2,2])
  x3_npcbgps_se <- sqrt(x3_npcbgps$cov.unscaled[2,2])
  x4_npcbgps_se <- sqrt(x4_npcbgps$cov.unscaled[2,2])
  x5_npcbgps_se <- sqrt(x5_npcbgps$cov.unscaled[2,2])
  x6_npcbgps_se <- sqrt(x6_npcbgps$cov.unscaled[2,2])
  
  # npcbgps coverage
  x1_npcbgps_cov <- (true_x1 > (x1_npcbgps$coefficient[2] - (1.96 * x1_npcbgps_se))) & 
    (true_x1 < (x1_npcbgps$coefficient[2] + (1.96 * x1_npcbgps_se)))
  x2_npcbgps_cov <- (true_x2 > (x2_npcbgps$coefficient[2] - (1.96 * x2_npcbgps_se))) & 
    (true_x2 < (x2_npcbgps$coefficient[2] + (1.96 * x2_npcbgps_se)))
  x3_npcbgps_cov <- (true_x3 > (x3_npcbgps$coefficient[2] - (1.96 * x3_npcbgps_se))) & 
    (true_x3 < (x3_npcbgps$coefficient[2] + (1.96 * x3_npcbgps_se)))
  x4_npcbgps_cov <- (true_x4 > (x4_npcbgps$coefficient[2] - (1.96 * x4_npcbgps_se))) & 
    (true_x4 < (x4_npcbgps$coefficient[2] + (1.96 * x4_npcbgps_se)))
  x5_npcbgps_cov <- (true_x5 > (x5_npcbgps$coefficient[2] - (1.96 * x5_npcbgps_se))) & 
    (true_x5 < (x5_npcbgps$coefficient[2] + (1.96 * x5_npcbgps_se)))
  x6_npcbgps_cov <- (true_x6 > (x6_npcbgps$coefficient[2] - (1.96 * x6_npcbgps_se))) & 
    (true_x6 < (x6_npcbgps$coefficient[2] + (1.96 * x6_npcbgps_se)))
  
  # qb10
  x1_qb10_bias <- true_x1 - x1_qb10$coefficient[2]
  x2_qb10_bias <- true_x2 - x2_qb10$coefficient[2]
  x3_qb10_bias <- true_x3 - x3_qb10$coefficient[2]
  
  # qb10 se
  x1_qb10_se <- sqrt(x1_qb10$cov.unscaled[2,2])
  x2_qb10_se <- sqrt(x2_qb10$cov.unscaled[2,2])
  x3_qb10_se <- sqrt(x3_qb10$cov.unscaled[2,2])
  
  # qb10 coverage
  x1_qb10_cov <- (true_x1 > (x1_qb10$coefficient[2] - (1.96 * x1_qb10_se))) & 
    (true_x1 < (x1_qb10$coefficient[2] + (1.96 * x1_qb10_se)))
  x2_qb10_cov <- (true_x2 > (x2_qb10$coefficient[2] - (1.96 * x2_qb10_se))) & 
    (true_x2 < (x2_qb10$coefficient[2] + (1.96 * x2_qb10_se)))
  x3_qb10_cov <- (true_x3 > (x3_qb10$coefficient[2] - (1.96 * x3_qb10_se))) & 
    (true_x3 < (x3_qb10$coefficient[2] + (1.96 * x3_qb10_se)))
  
  # qb15
  x1_qb15_bias <- true_x1 - x1_qb15$coefficient[2]
  x2_qb15_bias <- true_x2 - x2_qb15$coefficient[2]
  x3_qb15_bias <- true_x3 - x3_qb15$coefficient[2]
  
  #qb15 se
  x1_qb15_se <- sqrt(x1_qb15$cov.unscaled[2,2])
  x2_qb15_se <- sqrt(x2_qb15$cov.unscaled[2,2])
  x3_qb15_se <- sqrt(x3_qb15$cov.unscaled[2,2])
  
  #_qb15 coverage
  x1_qb15_cov <- (true_x1 > (x1_qb15$coefficient[2] - (1.96 * x1_qb15_se))) & 
    (true_x1 < (x1_qb15$coefficient[2] + (1.96 * x1_qb15_se)))
  x2_qb15_cov <- (true_x2 > (x2_qb15$coefficient[2] - (1.96 * x2_qb15_se))) & 
    (true_x2 < (x2_qb15$coefficient[2] + (1.96 * x2_qb15_se)))
  x3_qb15_cov <- (true_x3 > (x3_qb15$coefficient[2] - (1.96 * x3_qb15_se))) & 
    (true_x3 < (x3_qb15$coefficient[2] + (1.96 * x3_qb15_se)))
  
  # qb20
  x1_qb20_bias <- true_x1 - x1_qb20$coefficient[2]
  x2_qb20_bias <- true_x2 - x2_qb20$coefficient[2]
  x3_qb20_bias <- true_x3 - x3_qb20$coefficient[2]
  
  #qb20 se
  x1_qb20_se <- sqrt(x1_qb20$cov.unscaled[2,2])
  x2_qb20_se <- sqrt(x2_qb20$cov.unscaled[2,2])
  x3_qb20_se <- sqrt(x3_qb20$cov.unscaled[2,2])
  
  #_qb20 coverage
  x1_qb20_cov <- (true_x1 > (x1_qb20$coefficient[2] - (1.96 * x1_qb20_se))) & 
    (true_x1 < (x1_qb20$coefficient[2] + (1.96 * x1_qb20_se)))
  x2_qb20_cov <- (true_x2 > (x2_qb20$coefficient[2] - (1.96 * x2_qb20_se))) & 
    (true_x2 < (x2_qb20$coefficient[2] + (1.96 * x2_qb20_se)))
  x3_qb20_cov <- (true_x3 > (x3_qb20$coefficient[2] - (1.96 * x3_qb20_se))) & 
    (true_x3 < (x3_qb20$coefficient[2] + (1.96 * x3_qb20_se)))
  
  # olr
  x1_olr_bias <- true_x1 - x1_olr$coefficient[2]
  x2_olr_bias <- true_x2 - x2_olr$coefficient[2]
  x3_olr_bias <- true_x3 - x3_olr$coefficient[2]
  x4_olr_bias <- true_x4 - x4_olr$coefficient[2]
  x5_olr_bias <- true_x5 - x5_olr$coefficient[2]
  x6_olr_bias <- true_x6 - x6_olr$coefficient[2]
  
  # olr se
  x1_olr_se <- sqrt(x1_olr$cov.unscaled[2,2])
  x2_olr_se <- sqrt(x2_olr$cov.unscaled[2,2])
  x3_olr_se <- sqrt(x3_olr$cov.unscaled[2,2])
  x4_olr_se <- sqrt(x4_olr$cov.unscaled[2,2])
  x5_olr_se <- sqrt(x5_olr$cov.unscaled[2,2])
  x6_olr_se <- sqrt(x6_olr$cov.unscaled[2,2])
  
  # olr coverage
  x1_olr_cov <- (true_x1 > (x1_olr$coefficient[2] - (1.96 * x1_olr_se))) & 
    (true_x1 < (x1_olr$coefficient[2] + (1.96 * x1_olr_se)))
  x2_olr_cov <- (true_x2 > (x2_olr$coefficient[2] - (1.96 * x2_olr_se))) & 
    (true_x2 < (x2_olr$coefficient[2] + (1.96 * x2_olr_se)))
  x3_olr_cov <- (true_x3 > (x3_olr$coefficient[2] - (1.96 * x3_olr_se))) & 
    (true_x3 < (x3_olr$coefficient[2] + (1.96 * x3_olr_se)))
  x4_olr_cov <- (true_x4 > (x4_olr$coefficient[2] - (1.96 * x4_olr_se))) & 
    (true_x4 < (x4_olr$coefficient[2] + (1.96 * x4_olr_se)))
  x5_olr_cov <- (true_x5 > (x5_olr$coefficient[2] - (1.96 * x5_olr_se))) & 
    (true_x5 < (x5_olr$coefficient[2] + (1.96 * x5_olr_se)))
  x6_olr_cov <- (true_x6 > (x6_olr$coefficient[2] - (1.96 * x6_olr_se))) & 
    (true_x6 < (x6_olr$coefficient[2] + (1.96 * x6_olr_se)))

  # bias via the Austin, 2018 approach
  
  # first have to generate probability of having each exposure decile in each model

  # unweighted
  x1_uw_qs <- map_dbl(x1_quants,
                   ~ predict(x1_uw,
                             newdata = .x,
                             type = "fitted"))
  x2_uw_qs <- map_dbl(x2_quants,
                   ~ predict(x2_uw,
                             newdata = .x,
                             type = "fitted"))
  x3_uw_qs <- map_dbl(x3_quants,
                   ~ predict(x3_uw,
                             newdata = .x,
                             type = "fitted"))
  x4_uw_qs <- map_dbl(x4_quants,
                   ~ predict(x4_uw,
                             newdata = .x,
                             type = "fitted"))
  x5_uw_qs <- map_dbl(x5_quants,
                   ~ predict(x5_uw,
                             newdata = .x,
                             type = "fitted"))
  x6_uw_qs <- map_dbl(x6_quants,
                   ~ predict(x6_uw,
                             newdata = .x,
                             type = "fitted"))
  
  # x1
  x1_uw_bias2 <- true2_x1_qs - x1_uw_qs
  
  # x2
  x2_uw_bias2 <- true2_x2_qs - x2_uw_qs
  
  # x3
  x3_uw_bias2 <- true2_x3_qs - x3_uw_qs
  
  # x4
  x4_uw_bias2 <- true2_x4_qs - x4_uw_qs
  
  # x5
  x5_uw_bias2 <- true2_x5_qs - x5_uw_qs
  
  # x6
  x6_uw_bias2 <- true2_x6_qs - x6_uw_qs

    # ols
  x1_ols_qs <- data.frame(predict(x1_ols,
                                  newdata = data.frame(x1 = x1_quants),
                                  type = "response"))$response
  x2_ols_qs <- data.frame(predict(x2_ols,
                                  newdata = data.frame(x2 = x2_quants),
                                  type = "response"))$response
  x3_ols_qs <- data.frame(predict(x3_ols,
                                  newdata = data.frame(x3 = x3_quants),
                                  type = "response"))$response
  x4_ols_qs <- data.frame(predict(x4_ols,
                                  newdata = data.frame(x4 = x4_quants),
                                  type = "response"))$response
  x5_ols_qs <- data.frame(predict(x5_ols,
                                  newdata = data.frame(x5 = x5_quants),
                                  type = "response"))$response
  x6_ols_qs <- data.frame(predict(x6_ols,
                                  newdata = data.frame(x6 = x6_quants),
                                  type = "response"))$response
  
  # x1
  x1_ols_bias2 <- true2_x1_qs - x1_ols_qs
  
  # x2
  x2_ols_bias2 <- true2_x2_qs - x2_ols_qs
  
  # x3
  x3_ols_bias2 <- true2_x3_qs - x3_ols_qs
  
  # x4
  x4_ols_bias2 <- true2_x4_qs - x4_ols_qs
  
  # x5
  x5_ols_bias2 <- true2_x5_qs - x5_ols_qs
  
  # x6
  x6_ols_bias2 <- true2_x6_qs - x6_ols_qs
  
  # cbgps
  x1_cbgps_qs <- data.frame(predict(x1_cbgps,
                                  newdata = data.frame(x1 = x1_quants),
                                  type = "response"))$response
  x2_cbgps_qs <- data.frame(predict(x2_cbgps,
                                  newdata = data.frame(x2 = x2_quants),
                                  type = "response"))$response
  x3_cbgps_qs <- data.frame(predict(x3_cbgps,
                                  newdata = data.frame(x3 = x3_quants),
                                  type = "response"))$response
  x4_cbgps_qs <- data.frame(predict(x4_cbgps,
                                  newdata = data.frame(x4 = x4_quants),
                                  type = "response"))$response
  x5_cbgps_qs <- data.frame(predict(x5_cbgps,
                                  newdata = data.frame(x5 = x5_quants),
                                  type = "response"))$response
  x6_cbgps_qs <- data.frame(predict(x6_cbgps,
                                  newdata = data.frame(x6 = x6_quants),
                                  type = "response"))$response
  
  # x1
  x1_cbgps_bias2 <- true2_x1_qs - x1_cbgps_qs
  
  # x2
  x2_cbgps_bias2 <- true2_x2_qs - x2_cbgps_qs
  
  # x3
  x3_cbgps_bias2 <- true2_x3_qs - x3_cbgps_qs
  
  # x4
  x4_cbgps_bias2 <- true2_x4_qs - x4_cbgps_qs
  
  # x5
  x5_cbgps_bias2 <- true2_x5_qs - x5_cbgps_qs
  
  # x6
  x6_cbgps_bias2 <- true2_x6_qs - x6_cbgps_qs
  
  # npcbgps
  x1_npcbgps_qs <- data.frame(predict(x1_npcbgps,
                                  newdata = data.frame(x1 = x1_quants),
                                  type = "response"))$response
  x2_npcbgps_qs <- data.frame(predict(x2_npcbgps,
                                  newdata = data.frame(x2 = x2_quants),
                                  type = "response"))$response
  x3_npcbgps_qs <- data.frame(predict(x3_npcbgps,
                                  newdata = data.frame(x3 = x3_quants),
                                  type = "response"))$response
  x4_npcbgps_qs <- data.frame(predict(x4_npcbgps,
                                  newdata = data.frame(x4 = x4_quants),
                                  type = "response"))$response
  x5_npcbgps_qs <- data.frame(predict(x5_npcbgps,
                                  newdata = data.frame(x5 = x5_quants),
                                  type = "response"))$response
  x6_npcbgps_qs <- data.frame(predict(x6_npcbgps,
                                  newdata = data.frame(x6 = x6_quants),
                                  type = "response"))$response
  
  # x1
  x1_npcbgps_bias2 <- true2_x1_qs - x1_npcbgps_qs
  
  # x2
  x2_npcbgps_bias2 <- true2_x2_qs - x2_npcbgps_qs
  
  # x3
  x3_npcbgps_bias2 <- true2_x3_qs - x3_npcbgps_qs
  
  # x4
  x4_npcbgps_bias2 <- true2_x4_qs - x4_npcbgps_qs
  
  # x5
  x5_npcbgps_bias2 <- true2_x5_qs - x5_npcbgps_qs
  
  # x6
  x6_npcbgps_bias2 <- true2_x6_qs - x6_npcbgps_qs
  
  # qb10
  x1_qb10_qs <- data.frame(predict(x1_qb10,
                                  newdata = data.frame(x1 = x1_quants),
                                  type = "response"))$response
  x2_qb10_qs <- data.frame(predict(x2_qb10,
                                  newdata = data.frame(x2 = x2_quants),
                                  type = "response"))$response
  x3_qb10_qs <- data.frame(predict(x3_qb10,
                                  newdata = data.frame(x3 = x3_quants),
                                  type = "response"))$response
  
  # x1
  x1_qb10_bias2 <- true2_x1_qs - x1_qb10_qs
  
  # x2
  x2_qb10_bias2 <- true2_x2_qs - x2_qb10_qs
  
  # x3
  x3_qb10_bias2 <- true2_x3_qs - x3_qb10_qs
  
  # qb15
  x1_qb15_qs <- data.frame(predict(x1_qb15,
                                  newdata = data.frame(x1 = x1_quants),
                                  type = "response"))$response
  x2_qb15_qs <- data.frame(predict(x2_qb15,
                                  newdata = data.frame(x2 = x2_quants),
                                  type = "response"))$response
  x3_qb15_qs <- data.frame(predict(x3_qb15,
                                  newdata = data.frame(x3 = x3_quants),
                                  type = "response"))$response
  
  # x1
  x1_qb15_bias2 <- true2_x1_qs - x1_qb15_qs
  
  # x2
  x2_qb15_bias2 <- true2_x2_qs - x2_qb15_qs
  
  # x3
  x3_qb15_bias2 <- true2_x3_qs - x3_qb15_qs
  
  # qb20
  x1_qb20_qs <- data.frame(predict(x1_qb20,
                                  newdata = data.frame(x1 = x1_quants),
                                  type = "response"))$response
  x2_qb20_qs <- data.frame(predict(x2_qb20,
                                  newdata = data.frame(x2 = x2_quants),
                                  type = "response"))$response
  x3_qb20_qs <- data.frame(predict(x3_qb20,
                                  newdata = data.frame(x3 = x3_quants),
                                  type = "response"))$response
  
  # x1
  x1_qb20_bias2 <- true2_x1_qs - x1_qb20_qs
  
  # x2
  x2_qb20_bias2 <- true2_x2_qs - x2_qb20_qs
  
  # x3
  x3_qb20_bias2 <- true2_x3_qs - x3_qb20_qs
  
  # olr
  x1_olr_qs <- data.frame(predict(x1_olr,
                                  newdata = data.frame(x1 = x1_quants),
                                  type = "response"))$response
  x2_olr_qs <- data.frame(predict(x2_olr,
                                  newdata = data.frame(x2 = x2_quants),
                                  type = "response"))$response
  x3_olr_qs <- data.frame(predict(x3_olr,
                                  newdata = data.frame(x3 = x3_quants),
                                  type = "response"))$response
  x4_olr_qs <- data.frame(predict(x4_olr,
                                  newdata = data.frame(x4 = x4_quants),
                                  type = "response"))$response
  x5_olr_qs <- data.frame(predict(x5_olr,
                                  newdata = data.frame(x5 = x5_quants),
                                  type = "response"))$response
  x6_olr_qs <- data.frame(predict(x6_olr,
                                  newdata = data.frame(x6 = x6_quants),
                                  type = "response"))$response
  
  # x1
  x1_olr_bias2 <- true2_x1_qs - x1_olr_qs
  
  # x2
  x2_olr_bias2 <- true2_x2_qs - x2_olr_qs
  
  # x3
  x3_olr_bias2 <- true2_x3_qs - x3_olr_qs
  
  # x4
  x4_olr_bias2 <- true2_x4_qs - x4_olr_qs
  
  # x5
  x5_olr_bias2 <- true2_x5_qs - x5_olr_qs
  
  # x6
  x6_olr_bias2 <- true2_x6_qs - x6_olr_qs
  
  # output dataframe
  bias1 <- data.frame(i,
             x1_uw_bias, x2_uw_bias, x3_uw_bias, x4_uw_bias, x5_uw_bias, x6_uw_bias,
             x1_ols_bias, x2_ols_bias, x3_ols_bias, x4_ols_bias, x5_ols_bias, x6_ols_bias,
             x1_cbgps_bias, x2_cbgps_bias, x3_cbgps_bias, x4_cbgps_bias, x5_cbgps_bias, x6_cbgps_bias,
             x1_npcbgps_bias, x2_npcbgps_bias, x3_npcbgps_bias, x4_npcbgps_bias, x5_npcbgps_bias, x6_npcbgps_bias,
             x1_qb10_bias, x2_qb10_bias, x3_qb10_bias, 
             x1_qb15_bias, x2_qb15_bias, x3_qb15_bias,
             x1_qb20_bias, x2_qb20_bias, x3_qb20_bias,
             x1_olr_bias, x2_olr_bias, x3_olr_bias, x4_olr_bias, x5_olr_bias, x6_olr_bias)
  
  se1 <- data.frame(i,
             x1_uw_se, x2_uw_se, x3_uw_se, x4_uw_se, x5_uw_se, x6_uw_se,
             x1_ols_se, x2_ols_se, x3_ols_se, x4_ols_se, x5_ols_se, x6_ols_se,
             x1_cbgps_se, x2_cbgps_se, x3_cbgps_se, x4_cbgps_se, x5_cbgps_se, x6_cbgps_se,
             x1_npcbgps_se, x2_npcbgps_se, x3_npcbgps_se, x4_npcbgps_se, x5_npcbgps_se, x6_npcbgps_se,
             x1_qb10_se, x2_qb10_se, x3_qb10_se, 
             x1_qb15_se, x2_qb15_se, x3_qb15_se,
             x1_qb20_se, x2_qb20_se, x3_qb20_se,
             x1_olr_se, x2_olr_se, x3_olr_se, x4_olr_se, x5_olr_se, x6_olr_se)
  
  cov1 <- data.frame(i,
             x1_uw_cov, x2_uw_cov, x3_uw_cov, x4_uw_cov, x5_uw_cov, x6_uw_cov,
             x1_ols_cov, x2_ols_cov, x3_ols_cov, x4_ols_cov, x5_ols_cov, x6_ols_cov,
             x1_cbgps_cov, x2_cbgps_cov, x3_cbgps_cov, x4_cbgps_cov, x5_cbgps_cov, x6_cbgps_cov,
             x1_npcbgps_cov, x2_npcbgps_cov, x3_npcbgps_cov, x4_npcbgps_cov, x5_npcbgps_cov, x6_npcbgps_cov,
             x1_qb10_cov, x2_qb10_cov, x3_qb10_cov, 
             x1_qb15_cov, x2_qb15_cov, x3_qb15_cov,
             x1_qb20_cov, x2_qb20_cov, x3_qb20_cov,
             x1_olr_cov, x2_olr_cov, x3_olr_cov, x4_olr_cov, x5_olr_cov, x6_olr_cov)
  
  bias2 <- data.frame(quantile = c(1:9), 
             x1_uw_bias2, x2_uw_bias2, x3_uw_bias2, x4_uw_bias2, x5_uw_bias2, x6_uw_bias2,
             x1_ols_bias2, x2_ols_bias2, x3_ols_bias2, x4_ols_bias2, x5_ols_bias2, x6_ols_bias2, 
             x1_cbgps_bias2, x2_cbgps_bias2, x3_cbgps_bias2, x4_cbgps_bias2, x5_cbgps_bias2, x6_cbgps_bias2,
             x1_npcbgps_bias2, x2_npcbgps_bias2, x3_npcbgps_bias2, x4_npcbgps_bias2, x5_npcbgps_bias2, x6_npcbgps_bias2, 
             x1_qb10_bias2, x2_qb10_bias2, x3_qb10_bias2, 
             x1_qb15_bias2, x2_qb15_bias2, x3_qb15_bias2, 
             x1_qb20_bias2, x2_qb20_bias2, x3_qb20_bias2, 
             x1_olr_bias2, x2_olr_bias2, x3_olr_bias2, x4_olr_bias2, x5_olr_bias2, x6_olr_bias2) %>% 
    pivot_wider(names_from = quantile,
                values_from = x1_uw_bias2:x6_olr_bias2)
  
  data.frame(bias1, se1, cov1, bias2)
}

# # get bias across all simulations
# bias <- map_df(sims, ~ bias_func(.x))

# run in parallel with furrr
plan(multisession, workers = 7)
bias <- future_map_dfr(sims, ~ bias_func(.x))
Save(bias)
```

## Dose Reponse Decile Approach

### Supplemental Figure 2.5 - Bias at Deciles

```{r austin_bias_loop, fig.width=20, fig.height=10}
Load(bias)
# function to plot austin bias plots
aus_bias_plot <- function(decile) {
  # make bias dataframes
  x1_bias2 <- bias %>%
    select(starts_with("x1") & contains("bias2") & ends_with(as.character(decile))) %>%
    gather(label, bias) %>%
    mutate(label = factor(label,
                          levels = c(paste0("x1_uw_bias2_", decile),
                                     paste0("x1_ols_bias2_", decile),
                                     paste0("x1_cbgps_bias2_", decile),
                                     paste0("x1_npcbgps_bias2_", decile),
                                     paste0("x1_qb10_bias2_", decile),
                                     paste0("x1_qb15_bias2_", decile),
                                     paste0("x1_qb20_bias2_", decile),
                                     paste0("x1_olr_bias2_", decile))))

  x2_bias2 <- bias %>%
    select(starts_with("x2") & contains("bias2") & ends_with(as.character(decile))) %>%
    gather(label, bias) %>%
    mutate(label = factor(label,
                          levels = c(paste0("x2_uw_bias2_", decile),
                                     paste0("x2_ols_bias2_", decile),
                                     paste0("x2_cbgps_bias2_", decile),
                                     paste0("x2_npcbgps_bias2_", decile),
                                     paste0("x2_qb10_bias2_", decile),
                                     paste0("x2_qb15_bias2_", decile),
                                     paste0("x2_qb20_bias2_", decile),
                                     paste0("x2_olr_bias2_", decile))))

  x3_bias2 <- bias %>%
    select(starts_with("x3") & contains("bias2") & ends_with(as.character(decile))) %>%
    gather(label, bias) %>%
    mutate(label = factor(label,
                          levels = c(paste0("x3_uw_bias2_", decile),
                                     paste0("x3_ols_bias2_", decile),
                                     paste0("x3_cbgps_bias2_", decile),
                                     paste0("x3_npcbgps_bias2_", decile),
                                     paste0("x3_qb10_bias2_", decile),
                                     paste0("x3_qb15_bias2_", decile),
                                     paste0("x3_qb20_bias2_", decile),
                                     paste0("x3_olr_bias2_", decile))))
  
  x4_bias2 <- bias %>%
    select(starts_with("x4") & contains("bias2") & ends_with(as.character(decile))) %>%
    gather(label, bias) %>%
    mutate(label = factor(label,
                          levels = c(paste0("x4_uw_bias2_", decile),
                                     paste0("x4_ols_bias2_", decile),
                                     paste0("x4_cbgps_bias2_", decile),
                                     paste0("x4_npcbgps_bias2_", decile),
                                     paste0("x4_olr_bias2_", decile))))
  
  x5_bias2 <- bias %>%
    select(starts_with("x5") & contains("bias2") & ends_with(as.character(decile))) %>%
    gather(label, bias) %>%
    mutate(label = factor(label,
                          levels = c(paste0("x5_uw_bias2_", decile),
                                     paste0("x5_ols_bias2_", decile),
                                     paste0("x5_cbgps_bias2_", decile),
                                     paste0("x5_npcbgps_bias2_", decile),
                                     paste0("x5_olr_bias2_", decile))))
  
  x6_bias2 <- bias %>%
    select(starts_with("x6") & contains("bias2") & ends_with(as.character(decile))) %>%
    gather(label, bias) %>%
    mutate(label = factor(label,
                          levels = c(paste0("x6_uw_bias2_", decile),
                                     paste0("x6_ols_bias2_", decile),
                                     paste0("x6_cbgps_bias2_", decile),
                                     paste0("x6_npcbgps_bias2_", decile),
                                     paste0("x6_olr_bias2_", decile))))
  
  # make plots
  x1_bias_plot2 <- ggplot(x1_bias2, aes(y = fct_rev(label), x = bias)) +
    stat_halfeye() +
    geom_vline(xintercept = 0, alpha = 0.5, linetype = "dashed") +
    scale_y_discrete(name = "", labels = c("CPM", "QB20", "QB15", "QB10", "npCBGPS", "CBGPS", "OLS", "UW")) +
    scale_x_continuous(name = "Bias", limits = c(-0.125, 0.125), 
                       breaks = seq(-0.1, 0.1, 0.05), labels = seq(-0.1, 0.1, 0.05)) +
    theme +
    theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 24))

  x2_bias_plot2 <- ggplot(x2_bias2, aes(y = fct_rev(label), x = bias)) +
    stat_halfeye() +
    geom_vline(xintercept = 0, alpha = 0.5, linetype = "dashed") +
    scale_y_discrete(name = "", labels = c("CPM", "QB20", "QB15", "QB10", "npCBGPS", "CBGPS", "OLS", "UW")) +
    scale_x_continuous(name = "Bias", limits = c(-0.125, 0.125), 
                       breaks = seq(-0.1, 0.1, 0.05), labels = seq(-0.1, 0.1, 0.05)) +
    theme +
    theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 24))

  x3_bias_plot2 <- ggplot(x3_bias2, aes(y = fct_rev(label), x = bias)) +
    stat_halfeye() +
    geom_vline(xintercept = 0, alpha = 0.5, linetype = "dashed") +
    scale_y_discrete(name = "", labels = c("CPM", "QB20", "QB15", "QB10", "npCBGPS", "CBGPS", "OLS", "UW")) +
    scale_x_continuous(name = "Bias", limits = c(-0.125, 0.125), 
                       breaks = seq(-0.1, 0.1, 0.05), labels = seq(-0.1, 0.1, 0.05)) +
    theme +
    theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 24))
  
  x4_bias_plot2 <- ggplot(x4_bias2, aes(y = fct_rev(label), x = bias)) +
    stat_halfeye() +
    geom_vline(xintercept = 0, alpha = 0.5, linetype = "dashed") +
    scale_y_discrete(name = "", labels = c("CPM", "npCBGPS", "CBGPS", "OLS", "UW")) +
    scale_x_continuous(name = "Bias", limits = c(-0.125, 0.125), 
                       breaks = seq(-0.1, 0.1, 0.05), labels = seq(-0.1, 0.1, 0.05)) +
    theme +
    theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 24))
  
  x5_bias_plot2 <- ggplot(x5_bias2, aes(y = fct_rev(label), x = bias)) +
    stat_halfeye() +
    geom_vline(xintercept = 0, alpha = 0.5, linetype = "dashed") +
    scale_y_discrete(name = "", labels = c("CPM", "npCBGPS", "CBGPS", "OLS", "UW")) +
    scale_x_continuous(name = "Bias", limits = c(-0.125, 0.125), 
                       breaks = seq(-0.1, 0.1, 0.05), labels = seq(-0.1, 0.1, 0.05)) +
    theme +
    theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 24))
  
  x6_bias_plot2 <- ggplot(x6_bias2, aes(y = fct_rev(label), x = bias)) +
    stat_halfeye() +
    geom_vline(xintercept = 0, alpha = 0.5, linetype = "dashed") +
    scale_y_discrete(name = "", labels = c("CPM", "npCBGPS", "CBGPS", "OLS", "UW")) +
    scale_x_continuous(name = "Bias", limits = c(-0.125, 0.125), 
                       breaks = seq(-0.1, 0.1, 0.05), labels = seq(-0.1, 0.1, 0.05)) +
    theme +
    theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 24))

# combine plots
  ggarrange(x1_bias_plot2, x2_bias_plot2, x3_bias_plot2,
            x4_bias_plot2, x5_bias_plot2, x6_bias_plot2,
            labels = c(paste0("A", decile), paste0("B", decile), paste0("C", decile),
                       paste0("D", decile), paste0("E", decile), paste0("F", decile)), 
            font.label = list(size = 28),
            nrow = 1)
}

# plot all deciles
aus_plots <- map(c(1:9), ~ aus_bias_plot(.x))

# plots in chunks
ggarrange(aus_plots[[1]], aus_plots[[2]], aus_plots[[3]], ncol = 1)
#ggsave("./sim_png/supfig1.5_1.png")
ggarrange(aus_plots[[4]], aus_plots[[5]], aus_plots[[6]], ncol = 1)
#ggsave("./sim_png/supfig1.5_2.png")
ggarrange(aus_plots[[7]], aus_plots[[8]], aus_plots[[9]], ncol = 1)
#ggsave("./sim_png/supfig1.5_3.png")
```

Figure legend: Column A) Homoscedastic Exposure, Conditionally Normal, Marginally Normal, Column B) Homoscedastic Exposure, Conditionally Normal, Marginally Non-Normal, Column C) Heteroscedastic Exposure, Conditionally Non-Normal, Marginally Non-Normal. The number next to each panel represents the decile, such that "A1" is the 1st decile of the Homoscedastic, Conditionally Normal, Marginally Normal Exposure.

### Supplemental Figure 2.6 - Mean Squared Error at Deciles

```{r fig5, fig.width=7, fig.height=6}
# calculate mse for each scenario
austin_mse <- expand_grid(Decile = c(1:9),
                          Method = c("UW",
                                     "OLS",
                                     "CBGPS",
                                     "npCBGPS",
                                     "QB10",
                                     "QB15",
                                     "QB20",
                                     "OLR"),
                          Exposure = c("x1",
                                       "x2",
                                       "x3",
                                       "x4",
                                       "x5",
                                       "x6"),
                          MSE = NA)

# now loop through and fill in cells
for(i in 1:nrow(austin_mse)){
  # create column name of bias tibble
  col_name <- paste0(austin_mse$Exposure[i], "_", 
                     tolower(austin_mse$Method[i]), "_bias2_",
                     austin_mse$Decile[i])
  austin_mse$MSE[i] <- mean(bias[[col_name]]^2)
}

# Marginal Log Odds Ratio

mlor_mse <- expand_grid(Decile = c(0),
                          Method = c("UW",
                                     "OLS",
                                     "CBGPS",
                                     "npCBGPS",
                                     "QB10",
                                     "QB15",
                                     "QB20",
                                     "OLR"),
                          Exposure = c("x1",
                                       "x2",
                                       "x3",
                                       "x4",
                                       "x5",
                                       "x6"),
                          MSE = NA)

# now loop through and fill in cells
for(i in 1:nrow(mlor_mse)){
  # create column name of bias tibble
  col_name <- paste0(mlor_mse$Exposure[i], "_", 
                     tolower(mlor_mse$Method[i]), "_bias")
  mlor_mse$MSE[i] <- mean(bias[[col_name]]^2)
}

# now combine
mse_plot <- bind_rows(austin_mse, mlor_mse) %>%
  mutate(Method = ifelse(Method == "OLR", "CPM", Method),
         Type = ifelse(Decile == 0, "MLOR", "Decile"))

# now make plot

# first update levels
mse_plot <- mse_plot %>%
  mutate(Decile = factor(Decile),
         Method = factor(Method, levels = c("UW",
                                            "QB10",
                                     "OLS",
                                     "QB15",
                                     "CBGPS",
                                     "QB20",
                                     "npCBGPS",
                                     "CPM")),
         Exposure = factor(Exposure, levels = c("x1",
                                       "x2",
                                       "x3",
                                       "x4",
                                       "x5",
                                       "x6"))) %>%
  mutate(name = factor(Exposure,
                       labels = c(expression(paste("A) ", X[1])),
                                  expression(paste("B) ", X[2])),
                                  expression(paste("C) ", X[3])),
                                  expression(paste("D) ", X[4])),
                                  expression(paste("E) ", X[5])),
                                  expression(paste("F) ", X[6])))))

# fig 2
mse_plot %>% filter(Decile != 0) %>%
  ggplot(aes(x = MSE, y = Decile)) +
  # geom_vline(data = msm_mse, 
  #            aes(xintercept = MSE, color = Method),
  #            linetype = "longdash", alpha = 0.9) +
  geom_point(aes(shape = Method, color = Method), size = 1) +
  facet_wrap(~name, ncol = 3, labeller = "label_parsed", scales = "free_x") +
  scale_color_grey(guide = guide_legend(nrow = 2)) +
  scale_shape_manual(values = 1:nlevels(mse_plot$Method)) +
  #scale_y_continuous(name = "Decile", breaks = 1:9) + # if you'd like to jitter things
  theme +
  theme(panel.grid.major.y = element_line(),
        axis.text = element_text(size = 12, angle = 90),
        axis.title = element_text(size = 16),
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 14),
        strip.text = element_text(hjust = 0, size = 18),
        strip.background = element_blank())

# save plot
#ggsave("./sim_png/supfig1.6.png")
```

## Marginal Log Odds Ratio Approach

### Figure 2 - Marginal Log Odds Ratio Approach Bias

```{r fig2_fin, fig.width=6, fig.height=6, eval = FALSE}
# make df of x1:4 biases
x1_bias <- bias %>%
  select(starts_with("x1") & ends_with("bias")) %>%
  gather(label, bias) %>%
  mutate(label = factor(label,
                        levels = c("x1_uw_bias",
                                   "x1_ols_bias",
                                   "x1_cbgps_bias",
                                   "x1_npcbgps_bias",
                                   "x1_qb10_bias",
                                   "x1_qb15_bias",
                                   "x1_qb20_bias",
                                   "x1_olr_bias")),
         facet = str_sub(label, 1, 2),
         lab = str_sub(label, 4))

x2_bias <- bias %>%
  select(starts_with("x2") & ends_with("bias")) %>%
  gather(label, bias) %>%
  mutate(label = factor(label,
                        levels = c("x2_uw_bias",
                                   "x2_ols_bias",
                                   "x2_cbgps_bias",
                                   "x2_npcbgps_bias",
                                   "x2_qb10_bias",
                                   "x2_qb15_bias",
                                   "x2_qb20_bias",
                                   "x2_olr_bias")),
         facet = str_sub(label, 1, 2),
         lab = str_sub(label, 4))

x3_bias <- bias %>%
  select(starts_with("x3") & ends_with("bias")) %>%
  gather(label, bias) %>%
  mutate(label = factor(label,
                        levels = c("x3_uw_bias",
                                   "x3_ols_bias",
                                   "x3_cbgps_bias",
                                   "x3_npcbgps_bias",
                                   "x3_qb10_bias",
                                   "x3_qb15_bias",
                                   "x3_qb20_bias",
                                   "x3_olr_bias")),
         facet = str_sub(label, 1, 2),
         lab = str_sub(label, 4))

x4_bias <- bias %>%
  select(starts_with("x4") & ends_with("bias")) %>%
  gather(label, bias) %>%
  mutate(label = factor(label,
                        levels = c("x4_uw_bias",
                                   "x4_ols_bias",
                                   "x4_cbgps_bias",
                                   "x4_npcbgps_bias",
                                   "x4_olr_bias")),
         facet = str_sub(label, 1, 2),
         lab = str_sub(label, 4))

x5_bias <- bias %>%
  select(starts_with("x5") & ends_with("bias")) %>%
  gather(label, bias) %>%
  mutate(label = factor(label,
                        levels = c("x5_uw_bias",
                                   "x5_ols_bias",
                                   "x5_cbgps_bias",
                                   "x5_npcbgps_bias",
                                   "x5_olr_bias")),
         facet = str_sub(label, 1, 2),
         lab = str_sub(label, 4))

x6_bias <- bias %>%
  select(starts_with("x6") & ends_with("bias")) %>%
  gather(label, bias) %>%
  mutate(label = factor(label,
                        levels = c("x6_uw_bias",
                                   "x6_ols_bias",
                                   "x6_cbgps_bias",
                                   "x6_npcbgps_bias",
                                   "x6_olr_bias")),
         facet = str_sub(label, 1, 2),
         lab = str_sub(label, 4))

# combine into one dataset so can make facet plot
mse_bias_plot <- bind_rows(x1_bias, x2_bias, x3_bias, x4_bias, x5_bias, x6_bias) %>%
  mutate(facet = factor(facet, levels = c("x1", "x2", "x3", "x4", "x5", "x6")),
         lab = factor(lab,levels = c("uw_bias",
                                   "ols_bias",
                                   "cbgps_bias",
                                   "npcbgps_bias",
                                   "qb10_bias",
                                   "qb15_bias",
                                   "qb20_bias",
                                   "olr_bias"))) %>%
  mutate(name = factor(facet,
                       labels = c(expression(paste("A) ", X[1])),
                                  expression(paste("B) ", X[2])),
                                  expression(paste("C) ", X[3])),
                                  expression(paste("D) ", X[4])),
                                  expression(paste("E) ", X[5])),
                                  expression(paste("F) ", X[6])))))

# now plot with both austin and molr mse...
fig2_func <- function(exp_num, letter) {
  
  if(exp_num < 4) {
    mse_bias_plot %>% filter(facet == paste0("x", exp_num)) %>%
      ggplot(aes(y = fct_rev(lab), x = bias)) +
      stat_halfeye() +
      geom_vline(xintercept = 0, alpha = 0.5, linetype = "dashed") +
      scale_y_discrete(name = "", labels = c("CPM", "QB20", "QB15", "QB10", "npCBGPS", "CBGPS", "OLS", "UW"),) +
      scale_x_continuous(name = "Bias", limits = c(-0.25, 0.25), 
                      breaks = seq(-0.2, 0.2, 0.1), labels = seq(-0.2, 0.2, 0.1)) +
      annotate(geom = "text", x = 0.2, y = 9, label = "MSE", size = 10 / .pt) +
      annotate(geom = "text", x = 0.2, y = 8.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "UW") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 7.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "OLS") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 6.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "CBGPS") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 5.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "npCBGPS") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 4.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "QB10") %>% 
                pull(MSE) %>% round(4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 3.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "QB15") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 2.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "QB20") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 1.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "OLR") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      ggtitle(bquote(.(letter) * ") " ~ X[.(exp_num)])) +
      coord_cartesian(clip = "off") +
      theme +
      theme(panel.grid.major.y = element_line(),
            axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.position = "none")
  } else {
    mse_bias_plot %>% filter(facet == paste0("x", exp_num)) %>%
      ggplot(aes(y = fct_rev(lab), x = bias)) +
      stat_halfeye() +
      geom_vline(xintercept = 0, alpha = 0.5, linetype = "dashed") +
      scale_y_discrete(name = "", labels = c("CPM", "npCBGPS", "CBGPS", "OLS", "UW")) +
      scale_x_continuous(name = "Bias", limits = c(-0.25, 0.25), 
                      breaks = seq(-0.2, 0.2, 0.1), labels = seq(-0.2, 0.2, 0.1)) +
      annotate(geom = "text", x = 0.2, y = 6, label = "MSE", size = 10 / .pt) +
     annotate(geom = "text", x = 0.2, y = 5.5, label = mlor_mse %>% 
                 filter(Exposure == paste0("x", exp_num) & Method == "UW") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 4.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "OLS") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 3.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "CBGPS") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 2.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "npCBGPS") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      annotate(geom = "text", x = 0.2, y = 1.5, label = mlor_mse %>% 
                filter(Exposure == paste0("x", exp_num) & Method == "OLR") %>% 
                pull(MSE) %>% round(4) %>% format(nsmall = 4), size = 9 / .pt) +
      ggtitle(bquote(.(letter) * ") " ~ X[.(exp_num)])) +
      coord_cartesian(clip = "off") +
      theme +
      theme(panel.grid.major.y = element_line(),
            axis.text = element_text(size = 8),
            axis.title = element_text(size = 9),
            legend.position = "none")
  }
}

ggarrange(fig2_func(1, "A"),
          fig2_func(2, "B"),
          fig2_func(3, "C"),
          fig2_func(4, "D"),
          fig2_func(5, "E"),
          fig2_func(6, "F"),
          ncol = 3,
          nrow = 2,
          heights = c(8, 5),
          align= "hv")

# save plot
ggsave("figs/fig2.pdf", width = 7, height = 7)
# embed the font
embed_fonts("figs/fig2.pdf")
```

### Mean Squared Error

## Table 3 - Marginal Log Odds Ratio Approach Standard Error Ratio and Coverage

```{r tab3, eval = FALSE}
# now make table of mean squared error, which is the mean of the squared biases (or errors)
tab3 <- tibble(Method = c("Unweighted",
                            "Standard Error Ratio",
                            "Coverage",
                          "Ordinary least squares",
                            "Standard Error Ratio",
                            "Coverage",
                          "Covariate balancing generalized propensity score",
                            "Standard Error Ratio",
                            "Coverage",
                          "Non-parametric covariate balancing generalized propensity score",
                            "Standard Error Ratio",
                            "Coverage",
                          "Quantile binning categories",
                          "10",
                            "Standard Error Ratio",
                            "Coverage",
                          "15",
                            "Standard Error Ratio",
                            "Coverage",
                          "20",
                            "Standard Error Ratio",
                            "Coverage",
                          "Ordinal logistic regression",
                            "Standard Error Ratio",
                            "Coverage"),
               `X1` = c(NA, 
                        mean(bias$x1_uw_se) / sd(true_x1 - bias$x1_uw_bias),
                        mean(bias$x1_uw_cov),
                        NA, 
                        mean(bias$x1_ols_se) / sd(true_x1 - bias$x1_ols_bias),
                        mean(bias$x1_ols_cov),
                        NA,  
                        mean(bias$x1_cbgps_se) / sd(true_x1 - bias$x1_cbgps_bias),
                        mean(bias$x1_cbgps_cov),
                        NA, 
                        mean(bias$x1_npcbgps_se) / sd(true_x1 - bias$x1_npcbgps_bias),
                        mean(bias$x1_npcbgps_cov),
                        NA,
                        NA, 
                        mean(bias$x1_qb10_se) / sd(true_x1 - bias$x1_qb10_bias),
                        mean(bias$x1_qb10_cov),
                        NA, 
                        mean(bias$x1_qb15_se) / sd(true_x1 - bias$x1_qb15_bias),
                        mean(bias$x1_qb15_cov),
                        NA, 
                        mean(bias$x1_qb20_se) / sd(true_x1 - bias$x1_qb20_bias),
                        mean(bias$x1_qb20_cov),
                        NA,  
                        mean(bias$x1_olr_se) / sd(true_x1 - bias$x1_olr_bias),
                        mean(bias$x1_olr_cov)),
               `X4` = c(NA,  
                        mean(bias$x4_uw_se) / sd(true_x4 - bias$x4_uw_bias),
                        mean(bias$x4_uw_cov),
                        NA, 
                        mean(bias$x4_ols_se) / sd(true_x4 - bias$x4_ols_bias),
                        mean(bias$x4_ols_cov),
                        NA,  
                        mean(bias$x4_cbgps_se) / sd(true_x4 - bias$x4_cbgps_bias),
                        mean(bias$x4_cbgps_cov),
                        NA,  
                        mean(bias$x4_npcbgps_se) / sd(true_x4 - bias$x4_npcbgps_bias),
                        mean(bias$x4_npcbgps_cov),
                        NA,
                        NA, NA, NA,
                        NA, NA, NA,
                        NA, NA, NA,
                        NA,  
                        mean(bias$x4_olr_se) / sd(true_x4 - bias$x4_olr_bias),
                        mean(bias$x4_olr_cov)),
               `X2` = c(NA, 
                        mean(bias$x2_uw_se) / sd(true_x2 - bias$x2_uw_bias),
                        mean(bias$x2_uw_cov),
                        NA, 
                        mean(bias$x2_ols_se) / sd(true_x2 - bias$x2_ols_bias),
                        mean(bias$x2_ols_cov),
                        NA,  
                        mean(bias$x2_cbgps_se) / sd(true_x2 - bias$x2_cbgps_bias),
                        mean(bias$x2_cbgps_cov),
                        NA, 
                        mean(bias$x2_npcbgps_se) / sd(true_x2 - bias$x2_npcbgps_bias),
                        mean(bias$x2_npcbgps_cov),
                        NA,
                        NA, 
                        mean(bias$x2_qb10_se) / sd(true_x2 - bias$x2_qb10_bias),
                        mean(bias$x2_qb10_cov),
                        NA, 
                        mean(bias$x2_qb15_se) / sd(true_x2 - bias$x2_qb15_bias),
                        mean(bias$x2_qb15_cov),
                        NA, 
                        mean(bias$x2_qb20_se) / sd(true_x2 - bias$x2_qb20_bias),
                        mean(bias$x2_qb20_cov),
                        NA,  
                        mean(bias$x2_olr_se) / sd(true_x2 - bias$x2_olr_bias),
                        mean(bias$x2_olr_cov)),
               `X5` = c(NA,  
                        mean(bias$x5_uw_se) / sd(true_x5 - bias$x5_uw_bias),
                        mean(bias$x5_uw_cov),
                        NA, 
                        mean(bias$x5_ols_se) / sd(true_x5 - bias$x5_ols_bias),
                        mean(bias$x5_ols_cov),
                        NA,  
                        mean(bias$x5_cbgps_se) / sd(true_x5 - bias$x5_cbgps_bias),
                        mean(bias$x5_cbgps_cov),
                        NA,  
                        mean(bias$x5_npcbgps_se) / sd(true_x5 - bias$x5_npcbgps_bias),
                        mean(bias$x5_npcbgps_cov),
                        NA,
                        NA, NA, NA,
                        NA, NA, NA,
                        NA, NA, NA,
                        NA,  
                        mean(bias$x5_olr_se) / sd(true_x5 - bias$x5_olr_bias),
                        mean(bias$x5_olr_cov)),
               `X3` = c(NA, 
                        mean(bias$x3_uw_se) / sd(true_x3 - bias$x3_uw_bias),
                        mean(bias$x3_uw_cov),
                        NA, 
                        mean(bias$x3_ols_se) / sd(true_x3 - bias$x3_ols_bias),
                        mean(bias$x3_ols_cov),
                        NA,  
                        mean(bias$x3_cbgps_se) / sd(true_x3 - bias$x3_cbgps_bias),
                        mean(bias$x3_cbgps_cov),
                        NA,  
                        mean(bias$x3_npcbgps_se) / sd(true_x3 - bias$x3_npcbgps_bias),
                        mean(bias$x3_npcbgps_cov),
                        NA,
                        NA, 
                        mean(bias$x3_qb10_se) / sd(true_x3 - bias$x3_qb10_bias),
                        mean(bias$x3_qb10_cov),
                        NA, 
                        mean(bias$x3_qb15_se) / sd(true_x3 - bias$x3_qb15_bias),
                        mean(bias$x3_qb15_cov),
                        NA, 
                        mean(bias$x3_qb20_se) / sd(true_x3 - bias$x3_qb20_bias),
                        mean(bias$x3_qb20_cov),
                        NA,  
                        mean(bias$x3_olr_se) / sd(true_x3 - bias$x3_olr_bias),
                        mean(bias$x3_olr_cov)),
               `X6` = c(NA,  
                        mean(bias$x6_uw_se) / sd(true_x6 - bias$x6_uw_bias),
                        mean(bias$x6_uw_cov),
                        NA, 
                        mean(bias$x6_ols_se) / sd(true_x6 - bias$x6_ols_bias),
                        mean(bias$x6_ols_cov),
                        NA,  
                        mean(bias$x6_cbgps_se) / sd(true_x6 - bias$x6_cbgps_bias),
                        mean(bias$x6_cbgps_cov),
                        NA,  
                        mean(bias$x6_npcbgps_se) / sd(true_x6 - bias$x6_npcbgps_bias),
                        mean(bias$x6_npcbgps_cov),
                        NA,
                        NA, NA, NA,
                        NA, NA, NA,
                        NA, NA, NA,
                        NA,  
                        mean(bias$x6_olr_se) / sd(true_x6 - bias$x6_olr_bias),
                        mean(bias$x6_olr_cov))
               )

# make table
kable(tab3, digits = 3) %>%
  kable_classic(html_font = "Arial", full_width = FALSE) %>%
  add_header_above(c("Marginally", "Normal" = 2, "Non-Normal" = 2, 
                     "Non-Normal" = 2), bold = TRUE) %>%
  add_header_above(c("Conditionally", "Normal" = 2, "Normal" = 2, 
                     "Non-Normal" = 2), bold = TRUE) %>%
  add_indent(c(2:3, 5:6, 8:9, 11:12, 15:16, 18:19, 21:22, 24:25)) %>%
  add_indent(c(2:3, 5:6, 8:9, 11:12, 13:22, 24:25))
```

### Supplemental Table 2.5 - Marginal Log Odds Ratio Approach Bias

```{r tab4}
# now make table of biases
tab4 <- tibble(Method = c("Unweighted",
                          "Ordinary least squares",
                          "Covariate balancing generalized propensity score",
                          "Non-parametric covariate balancing generalized propensity score",
                          "Quantile binning categories",
                          "10",
                          "15",
                          "20",
                          "Ordinal logistic regression"),
               `Median Bias (IQR)` = c(paste0(round(median(bias$x1_uw_bias), 4), " (",
                                            round(quantile(bias$x1_uw_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x1_uw_bias, 0.75), 3), ")"),
                                       paste0(round(median(bias$x1_ols_bias), 4), " (",
                                            round(quantile(bias$x1_ols_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x1_ols_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x1_cbgps_bias), 4), " (",
                                            round(quantile(bias$x1_cbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x1_cbgps_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x1_npcbgps_bias), 4), " (",
                                            round(quantile(bias$x1_npcbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x1_npcbgps_bias, 0.75), 3), ")"),
                                     NA,
                                     paste0(round(median(bias$x1_qb10_bias), 4), " (",
                                            round(quantile(bias$x1_qb10_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x1_qb10_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x1_qb15_bias), 4), " (",
                                            round(quantile(bias$x1_qb15_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x1_qb15_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x1_qb20_bias), 4), " (",
                                            round(quantile(bias$x1_qb20_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x1_qb20_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x1_olr_bias), 4), " (",
                                            round(quantile(bias$x1_olr_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x1_olr_bias, 0.75), 3), ")")),
               `Median Bias (IQR)   ` = c(paste0(round(median(bias$x4_uw_bias), 4), " (",
                                            round(quantile(bias$x4_uw_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x4_uw_bias, 0.75), 3), ")"),
                                       paste0(round(median(bias$x4_ols_bias), 4), " (",
                                            round(quantile(bias$x4_ols_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x4_ols_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x4_cbgps_bias), 4), " (",
                                            round(quantile(bias$x4_cbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x4_cbgps_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x4_npcbgps_bias), 4), " (",
                                            round(quantile(bias$x4_npcbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x4_npcbgps_bias, 0.75), 3), ")"),
                                     NA,
                                     NA,
                                     NA,
                                     NA,
                                     paste0(round(median(bias$x4_olr_bias), 4), " (",
                                            round(quantile(bias$x4_olr_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x4_olr_bias, 0.75), 3), ")")),
               `Median Bias (IQR) ` = c(paste0(round(median(bias$x2_uw_bias), 4), " (",
                                            round(quantile(bias$x2_uw_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x2_uw_bias, 0.75), 3), ")"),
                                        paste0(round(median(bias$x2_ols_bias), 4), " (",
                                            round(quantile(bias$x2_ols_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x2_ols_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x2_cbgps_bias), 4), " (",
                                            round(quantile(bias$x2_cbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x2_cbgps_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x2_npcbgps_bias), 4), " (",
                                            round(quantile(bias$x2_npcbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x2_npcbgps_bias, 0.75), 3), ")"),
                                     NA,
                                     paste0(round(median(bias$x2_qb10_bias), 4), " (",
                                            round(quantile(bias$x2_qb10_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x2_qb10_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x2_qb15_bias), 4), " (",
                                            round(quantile(bias$x2_qb15_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x2_qb15_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x2_qb20_bias), 4), " (",
                                            round(quantile(bias$x2_qb20_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x2_qb20_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x2_olr_bias), 4), " (",
                                            round(quantile(bias$x2_olr_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x2_olr_bias, 0.75), 3), ")")),
               `Median Bias (IQR)    ` = c(paste0(round(median(bias$x5_uw_bias), 4), " (",
                                            round(quantile(bias$x5_uw_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x5_uw_bias, 0.75), 3), ")"),
                                       paste0(round(median(bias$x5_ols_bias), 4), " (",
                                            round(quantile(bias$x5_ols_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x5_ols_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x5_cbgps_bias), 4), " (",
                                            round(quantile(bias$x5_cbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x5_cbgps_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x5_npcbgps_bias), 4), " (",
                                            round(quantile(bias$x5_npcbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x5_npcbgps_bias, 0.75), 3), ")"),
                                     NA,
                                     NA,
                                     NA,
                                     NA,
                                     paste0(round(median(bias$x5_olr_bias), 4), " (",
                                            round(quantile(bias$x5_olr_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x5_olr_bias, 0.75), 3), ")")),
               `Median Bias (IQR)  ` = c(paste0(round(median(bias$x3_uw_bias), 4), " (",
                                            round(quantile(bias$x3_uw_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x3_uw_bias, 0.75), 3), ")"),
                                         paste0(round(median(bias$x3_ols_bias), 4), " (",
                                            round(quantile(bias$x3_ols_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x3_ols_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x3_cbgps_bias), 4), " (",
                                            round(quantile(bias$x3_cbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x3_cbgps_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x3_npcbgps_bias), 4), " (",
                                            round(quantile(bias$x3_npcbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x3_npcbgps_bias, 0.75), 3), ")"),
                                     NA,
                                     paste0(round(median(bias$x3_qb10_bias), 4), " (",
                                            round(quantile(bias$x3_qb10_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x3_qb10_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x3_qb15_bias), 4), " (",
                                            round(quantile(bias$x3_qb15_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x3_qb15_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x3_qb20_bias), 4), " (",
                                            round(quantile(bias$x3_qb20_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x3_qb20_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x3_olr_bias), 4), " (",
                                            round(quantile(bias$x3_olr_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x3_olr_bias, 0.75), 3), ")")),
               `Median Bias (IQR)     ` = c(paste0(round(median(bias$x6_uw_bias), 4), " (",
                                            round(quantile(bias$x6_uw_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x6_uw_bias, 0.75), 3), ")"),
                                       paste0(round(median(bias$x6_ols_bias), 4), " (",
                                            round(quantile(bias$x6_ols_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x6_ols_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x6_cbgps_bias), 4), " (",
                                            round(quantile(bias$x6_cbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x6_cbgps_bias, 0.75), 3), ")"),
                                     paste0(round(median(bias$x6_npcbgps_bias), 4), " (",
                                            round(quantile(bias$x6_npcbgps_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x6_npcbgps_bias, 0.75), 3), ")"),
                                     NA,
                                     NA,
                                     NA,
                                     NA,
                                     paste0(round(median(bias$x6_olr_bias), 4), " (",
                                            round(quantile(bias$x6_olr_bias, 0.25), 3), ", ",
                                            round(quantile(bias$x6_olr_bias, 0.75), 3), ")"))
               )

# make table
kable(tab4) %>%
  kable_classic(html_font = "Arial", full_width = TRUE) %>%
  add_header_above(c("", "X1" = 1, "X4" = 1, "X2" = 1, 
                     "X5" = 1, "X3" = 1, "X6" = 1), bold = TRUE) %>%
  add_header_above(c("Marginally", "Normal" = 2, "Non-Normal" = 2, 
                     "Non-Normal" = 2), bold = TRUE) %>%
  add_header_above(c("Conditionally", "Normal" = 2, "Normal" = 2, 
                     "Non-Normal" = 2), bold = TRUE) %>%
  add_indent(c(6:8))
```

# Session Info

```{r sess_info}
sessionInfo()
```

# References
